### 2018-03-26 Paper/cover.tex
adding files

\begin{center}
\textsc{
Facilitating Uncertainty Analysis in Non-Equilibrium Molecular Dynamics Simulations for
Thermal Transport
}

\bigskip 
\bigskip

Manav Vohra$^{1}$, Ali Y. Nobakht$^{2}$, Seungha Shin$^{2}$, Sankaran Mahadevan$^{1}$

\bigskip
\bigskip

\normalsize
$^1$Department of Civil and Environmental Engineering\\
Vanderbilt University\\
Nashville, TN 37235\\

\bigskip

$^2$Department of Mechanical, Aerospace, and Biomedical Engineering\\
The University of Tennessee\\
Knoxville, TN 37996\\

\bigskip

\end{center}

\vspace{6cm}

\begin{tabbing}
Corresponding Author: \hspace{5mm} \= Sankaran Mahadevan\\
       \>  Department of Civil and Environmental Engineering\\
       \>  Vanderbilt University\\
       \>  272 Jacobs Hall, VU Mailbox: PMB 351831 \\
       \>  Nashville, TN 37235 \\
       \> \\
Phone: \> (615) 322-3040 \\
Fax:   \> (615) 343-3773 \\
Email: \>  sankaran.mahadevan@vanderbilt.edu   \\
\\
Submitted to: \> \textit{International Journal of Heat and Mass Transfer} \\
\>  April 2018\\

\bigskip
\end{tabbing}

\clearpage

### 2018-03-26 Paper/intro.tex
adding files

\section{Introduction}
\label{sec:intro}

\begin{comment}
1. Background on use of MD simulations for thermal transport, preferred for studying
thermal transport by phononic interactions (refer notes from book suggested by Amuthan)

2. One approach to NEMD is the Direct Method, commonly used for estimating the bulk
thermal conductivity. A brief discussion on the direct method and associated pros and cons
(notes from Dellan's paper and book suggested by Amuthan) 
Predictions impacted by the choice of potential, values of
individual parameters, size, and potentially due to duration and applied thermal gradients
(cite Amuthan book, Francesco's paper, McGaughey's paper). 
Errors are introduced by thermostatting (Amuthan book). Nominal value of SW potential parameters based on fitting against experiments and to ensure structural stability etc. (SW paper)

3. Motivate uncertainty analysis and briefly discuss and cite recent efforts (Francesco, Kirby,
Murthy). Highlight focus and key contributions of the present work and how it differs from
those efforts.

4. Section-wise overview of the paper.  
\end{comment}

Classical Molecular Dynamics (MD) is commonly used to study thermal transport in material systems 
especially in situations where transport due to phonon-phonon interactions is predominant. These 
systems typically comprise non-metallic elements such as carbon (nanotubes, fullerenes, graphite, etc.),
silicon and germanium.

### 2018-03-26 Paper/intro.tex
...

@@
 
-Classical Molecular Dynamics (MD) is commonly used to study thermal transport in material systems 
-especially in situations where transport due to phonon-phonon interactions is predominant. These 
-systems typically comprise non-metallic elements such as carbon (nanotubes, fullerenes, graphite, etc.),
-silicon and germanium.
+Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of phonons in material 
+systems comprising non-metallic elements such as carbon, silicon, germanium.

### 2018-03-26 Paper/intro.tex
paper

@@
 
-Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of phonons in material 
-systems comprising non-metallic elements such as carbon, silicon, germanium.
+Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of
+interactions between phonons in material systems comprising non-metallic elements such
+as carbon, silicon, and germanium~\cite{Dumitrica:2010}. 
+A major objective for many such studies is the
+estimation of bulk thermal conductivity of the system. One of the most commonly used approach,
+regarded as the direct method~\cite{Schelling:2002,Turney:2009,Zhou:2009,Landry:2009,
+McGaughey:2006,Ni:2009,Shi:2009,Wang:2009,Papanikolaou:2008}, is a non-equilibrium
+technique that involves the application
+of a heat flux or a temperature gradient by means of thermostatting across the system. 
+Corresponding steady-state temperature gradient in the former or the heat exchange between
+the two thermostats in the latter, is used to estimate thermal conductivity (at a given
+length or size) using 
+Fourier's law. Computations are performed for a range of system lengths and the inverse
+of thermal conductivity is plotted against the inverse of length. The y-intercept of a
+straight line fit to the observed trend is considered as the bulk thermal conductivity 
+estimate.
+
+Although widely used, the direct method is khown to severly under-predict
+the bulk thermal conductivity as compared to experimental 
+measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
+due to length scales used in simulation that are several orders of magnitude smaller
+than those used in an experiment. As a result, the sample length is much smaller than the
+bulk phonon mean free path leading to a so-called ballistic transport of the phonons.
+The mean free path of such phonon modes is limited to the system size that reduces their
+contribution to thermal transport. Moreover, the
+introduction of thermostats typically reduces the correlation between vibrations of 
+different atoms (regarded as Kapitza effect~\cite{Stevens:2007}) potentially reducing
+the thermal conductivity
+further~\cite{Evans:2008}. Estimate of thermal conductivity using the
+direct method is therefore impacted by the choice of system size and potentially due to
+variability in the thermal gradient experienced by the system owing to
+Kapitza effect.
+
+Predictions of non-equilibrium molecular dynamics simulations (NEMD) are dependent on the
+choice of the inter-atomic potential as well as values associated with individual parameters
+of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
+is a widely used inter-atomic potential. However, as discussed by Stillinger and Weber
+in~\cite{Stillinger:1985}, the proposed nominal values of individual parameters were based
+on a limited search in the 7D parameter space while ensuring structural stability and
+reasonable agreement with experiments. It is therefore likely that these nominal estimates
+for individual parameter values in the SW potential may not yield accurate results for a
+wide variety of Si-based systems and warrants further investigation to study the impact of
+underlying uncertainties on MD predicitions.
+
+%In a recent effort, Rizzi et al. study the effect of
+%uncertainties associated with the force-field parameters on bulk water properties using MD
+%simulations~\cite{Rizzi:2012}.

### 2018-03-27 Paper/intro.tex
intro updated

@@
 
-Although widely used, the direct method is khown to severly under-predict
+Although widely used, the direct method is known to severely under-predict
 the bulk thermal conductivity as compared to experimental 
@@
 
-Predictions of non-equilibrium molecular dynamics simulations (NEMD) are dependent on the
+Predictions of non-equilibrium molecular dynamics (NEMD) simulations are dependent on the
 choice of the inter-atomic potential as well as values associated with individual parameters
@@
 for individual parameter values in the SW potential may not yield accurate results for a
-wide variety of Si-based systems and warrants further investigation to study the impact of
-underlying uncertainties on MD predicitions.
+wide variety of Si-based systems and warrant further investigation to study the impact of
+underlying uncertainties on MD predictions. 
+In a recent effort, Rizzi et al. study the effect of
+uncertainties associated with the force-field parameters on bulk water properties using MD
+simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} consider a stochastic model
+for thermal conductivity (due to noise in MD simulations) and study its impact on spatial temperature 
+distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implement an uncertainty
+quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
+ water. While these are significant contributions, it is only until recently 
+that researchers have started accounting for the presence of uncertainties in MD predictions in a
+systematic manner. There is a definite need for additional efforts aimed at efficiency and accuracy
+to enable uncertainty analysis in MD simulations for a wide range of applications.
 
-%In a recent effort, Rizzi et al. study the effect of
-%uncertainties associated with the force-field parameters on bulk water properties using MD
-%simulations~\cite{Rizzi:2012}.
+In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
+for phonon transport.  As discussed earlier, predictions from NEMD
+exhibit large discrepancies with experimental observations depending upon system size and potentially
+due to variability in the applied thermal gradient. Additionally, the thermal conductivity estimates are
+tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
+accomplish multiple objectives through this research effort: First, we construct response surfaces
+in order to characterize the dependence of discrepancy in thermal conductivity estimates from NEMD
+with the experimental data on system size and applied thermal gradient. Second, we perform
+sensitivity analysis to study the impact of SW potential parameter values on variability in predictions.
+Third, we exploit our findings from sensitivity analysis to discern parameters for calibration in a Bayesian
+setting in order to enhance the predictability of NEMD simulations.

### 2018-03-27 Paper/intro.tex
intro pass 1 complete

@@
 In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
-for phonon transport.  As discussed earlier, predictions from NEMD
+for phonon transport using a silicon bar. An overview of the set-up for the simulations is
+provided in Section~\ref{sec:setup}. As discussed earlier, predictions from NEMD
 exhibit large discrepancies with experimental observations depending upon system size and potentially
@@
 accomplish multiple objectives through this research effort: First, we construct response surfaces
-in order to characterize the dependence of discrepancy in thermal conductivity estimates from NEMD
-with the experimental data on system size and applied thermal gradient. Second, we perform
-sensitivity analysis to study the impact of SW potential parameter values on variability in predictions.
-Third, we exploit our findings from sensitivity analysis to discern parameters for calibration in a Bayesian
-setting in order to enhance the predictability of NEMD simulations.
+in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
+MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
+Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
+variability in predictions~(Section~\ref{sec:sense}).
+Third, we exploit our findings from sensitivity analysis to discern important parameters and hence
+reduce the dimensionality of the problem~(Section~\ref{sec:ros}). Fourth, we illustrate calibration
+of the important parameters in a Bayesian setting to evaluate their posterior
+distributions~(Section~\ref{sec:bayes}). Construction of the
+response surfaces, parametric sensitivity analysis, and Bayesian calibration can all be computationally
+challenging endeavors especially in situations involving compute-intensive simulations as in the
+case of NEMD. We therefore employ polynomial choas (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
+using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce computational effort pertaining
+to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
+expensive, we demonstrate in Section~\ref{sec:sense}, a novel approach that implements derivative-based
+sensitivity measures~\cite{Sobol:2010} to a priori reduce the dimensionality of the surrogate while
+ensuring reasonable predictive accuracy.

### 2018-03-27 Paper/ros.tex
intro pass 1 complete

\section{Reduced Order Surrogate}
\label{sec:ros}

### 2018-03-27 Paper/sense.tex
intro pass 1 complete

\section{Derivative-based Sensitivity Analysis}
\label{sec:sense}

### 2018-03-28 Paper/setup.tex
set up

\section{NEMD Set-up}
\label{sec:setup}

Non-equilibrium molecular dynamics (NEMD) simulations are performed in LAMMPS~\cite{Plimpton:2007}
by applying a thermal gradient by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$. 
The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}.

### 2018-03-29 Paper/setup.tex
...

@@
 by applying a thermal gradient by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$. 
-The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}.
+The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}. The set of
+inputs to LAMMPS is provided below in Table~1. Note that specific values for the length of the bar
+and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
+values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
+minimizing temperature fluctuations during different stages of the simulation was performed to optimize for the
+choice of height and width of the bar as well as the duration of the simulation.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{|c||c|}
+\hline
+Lattice Constant, $a$ ($\angstrom$) & 5.43 \\ \hline
+Width, Height ($\angstrom$) & 22$a$ \\ \hline
+$\Delta t$  (ps) & 0.0005 \\ \hline
+Boundary Condition & Periodic \\ \hline
+Lattice Structure & Diamond \\ \hline
+Inter-atomic Potential & Stillinger-Weber \\ 
+\hline
+\end{tabular}
+\end{center}
+\label{tab:input}
+\caption{Set of inputs for the NEMD simulation to estimate thermal conductivity in a Si bar using LAMMPS.}
+\end{table}
+
+There NEMD simulation has three stages associated with it as illustrated below in the flow diagram. In the
+first stage, the NVT ensemble equilibrates the system to a specified bulk temperature i.e. the temperature
+at which thermal conductivity is to be estimated. In the second stage, the NVE ensemble equilibrates the
+thermostats at their respective temperatures. It is followed by another NVE ensemble that captures the
+trajectory of individual atoms and results in a steady state estimate for the thermal energy exchange between
+the two thermostats.
+
+\begin{center}
+
+NVT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVE \hspace{5mm}
+$\rightarrow$ \hspace{5mm} NVE
+\\ \vspace{1mm}
+\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+ [Generate Data]
+\\ \vspace{1mm}
+
+\tiny{N: Number of Atoms~~~V: Volume~~~T: Temperature~~~E: Energy}
+\end{center}
+
+The steady state exchange energy ($q$) is used in Fourier's law to estimate bulk thermal conductivity ($\kappa$)
+for the Si  bar:
+
+\be
+ \kappa = \frac{q}{\left|\frac{dT}{dz}\right|} 
+\ee
+
+\noindent where $\left|\frac{dT}{dz}\right|$ denotes the magnitude of the applied temperature gradient along the 
+direction of heat flow (see~Figure~\ref{fig:setup}(a)).

### 2018-04-04 Paper/sense.tex
...
..

@@
-\section{Derivative-based Sensitivity Analysis}
+\section{Sensitivity Analysis of the Inter-atomic Potential}
 \label{sec:sense}
+
+As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD are dependent
+on the choice of the inter-atomic potential as well as values associated with the individual potential parameters.
+In the case of silicon, Stillinger-Weber is a commonly used potential and the proposed set of nominal values
+have been used for a wide variety of systems. According Stillinger and Weber, the set of nominal values as provided
+below in Table~\ref{tab:nom} is based on a constrained search in the 7D parameter space
+to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}. However, it is
+noteworthy that these estimates did not account for the presence of uncertainty due to experimental data, 
+inadequacies pertaining to the potential function, and parametric uncertainties. Hence, it is critical
+to understand the impact of such uncertainties on NEMD predictions for bulk thermal conductivity using
+SW potential.

### 2018-04-05 Paper/sense.tex
..

--- 2018-03-27 Paper/sense.tex
@@
-\section{Derivative-based Sensitivity Analysis}
+\section{Sensitivity Analysis of the Inter-atomic Potential}
 \label{sec:sense}
+
+As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD
+are dependent on the choice of the inter-atomic potential as well as values associated with
+the individual potential parameters. In the case of silicon, the Stillinger-Weber inter-atomic potential
+has been used for a wide variety of 
+systems~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein).
+However, according to Stillinger and Weber, the set of nominal
+values as provided below in Table~2 is based on a constrained search in the 7D parameter space
+to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.
+
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{|c||c|}
+\hline
+$A$ & 7.049556277 \\
+$B$ & 0.6022245584 \\
+$p$ & 4.0 \\
+$q$ & 0.0 \\
+$\alpha$ & 1.80 \\
+$\lambda$ & 21.0 \\
+$\gamma$ & 1.20 \\
+\hline
+\end{tabular}
+\end{center}
+\caption{Nominal values of the parameters of the Stillinger-Weber inter-atomic
+potential~\cite{Stillinger:1985}.}
+\end{table}
+
+It is noteworthy that the underlying analysis which lead to these estimates did not account for the
+presence of uncertainty due to
+measurement error, noise inherent in MD predictions, inadequacies pertaining to the potential function,
+and parametric uncertainties. It is therefore likely that the proposed nominal estimates could be 
+improved depending upon the application. Hence, it is critical to understand the effects of variability in
+SW potential parameters on buk thermal conductivity predictions using NEMD. For this purpose, a possible
+approach could involve a global sensitivity analysis of NEMD predictions on the SW potential parameters 
+by estimating the so-called Sobol indices~\cite{Sobol:2001}. However, obtaining converged estimates of
+Sobol indices typically requires tens of thousands of model evaluations. Since NEMD is compute-intensive,
+estimating the Sobol indices directly would be impractical. Instead, we adopt a novel strategy that
+aims to determine relative importance of the SW potential parameters based on derivative-based global 
+sensitivity measures (DGSM)~\cite{Sobol:2010}. In fact, it can be shown that the upper bound on a 
+Sobol index can be expressed in terms of DGSM~($\mu_i$), the Poincare constant~($\mathcal{C}_i$), and the
+total variance of the observed quantity~($V$)~\cite{Lamboni:2013,Roustant:2014}:

### 2018-04-05 Paper/sense.tex
..

@@
 \begin{center}
-\begin{tabular}{|c||c|}
+\begin{tabular}{|c|c|c|c|c|c|c|}
 \hline 
-$A$ & 7.049556277 \\
-$B$ & 0.6022245584 \\
-$p$ & 4.0 \\
-$q$ & 0.0 \\
-$\alpha$ & 1.80 \\
-$\lambda$ & 21.0 \\
-$\gamma$ & 1.20 \\
+$A$ & $B$ & $p$ & $q$ & $\alpha$ & $\lambda$ & $\gamma$ \\
+\hline \hline
+7.049556277 & 0.6022245584 & 4.0 & 0.0 & 1.80 & 21.0 & 1.20 \\
 \hline
@@
 
-It is noteworthy that the underlying analysis which lead to these estimates did not account for the
-presence of uncertainty due to
+It is noteworthy that the underlying analysis which lead to these estimates of the nominal values did not
+account for the presence of uncertainty due to
 measurement error, noise inherent in MD predictions, inadequacies pertaining to the potential function,
@@
 improved depending upon the application. Hence, it is critical to understand the effects of variability in
-SW potential parameters on buk thermal conductivity predictions using NEMD. For this purpose, a possible
+SW potential parameters on bulk thermal conductivity predictions using NEMD. For this purpose, a possible
 approach could involve a global sensitivity analysis of NEMD predictions on the SW potential parameters 
@@
 aims to determine relative importance of the SW potential parameters based on derivative-based global 
-sensitivity measures (DGSM)~\cite{Sobol:2010}. In fact, it can be shown that the upper bound on a 
-Sobol index can be expressed in terms of DGSM~($\mu_i$), the Poincare constant~($\mathcal{C}_i$), and the
-total variance of the observed quantity~($V$)~\cite{Lamboni:2013,Roustant:2014}:
+sensitivity measures (DGSM)~\cite{Sobol:2010}. It is observed that for a given application, it might be possible to 
+converge to the upper bound on
+Sobol index with only a few iterations~($\mathcal{O}(10^{1})$) thereby leading to enormous computational savings. 
+In that case, estimates of the upper bound could be used in lieu of the
+Sobol indices to determine relative importance of the parameters. The upper bound on 
+Sobol total effect index\footnote{Sobol total effect index is a measure of the contribution of a 
+parameter to the variance of the observable while contribution from other parameters may or may not be 0.}
+($\mathcal{T}_i$) can be expressed in terms of DGSM~($\mu_i$), the Poincar\' e 
+constant~($\mathcal{C}_i$), and the total variance of the observed
+quantity~($V$)~\cite{Lamboni:2013,Roustant:2014}:
+
+\be
+\mathcal{T}_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i}) 
+\ee
+
+\noindent The derivative-based sensitivity measure, $\mu_i$ for a given parameter, $\theta_i$ is defined as an expectation
+of the derivative of the observable ($G(\bm{\theta})$) with respect to that parameter:
+
+\be
+\mu_i = \mathbb{E}\left[\left(\frac{\partial G(\bm{\theta})}{\partial \theta_i}\right)^{2}\right]
+\label{eq:mu}
+\ee
+
+\noindent Latin hypercube sampling in the 7D parameter space is used to estimate $\mu_i$. Note that $G$ must 
+exhibit a smooth variation with each parameter so that the derivative in Eq.~\ref{eq:mu} can be estimated
+with reasonable accuracy either analytically or numerically. 
+ In this work, we examine the suitability of this
+approach based on DGSM for the present application involving thermal transport in bulk Si. We define a 
+normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:
+
+\be
+\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i} 
+\ee
+
+\noindent The choice of $\mathcal{C}_i$ is specific to the marginal probability distribution of the uncertain model
+parameter, $\theta_i$. In this work, we consider all uncertain parameters to be uniformly
+distributed in the interval~$[a,b]$ in which case $\mathcal{C}_i$  is given as $(b-a)^{2}/\pi^2$~\cite{Roustant:2014}.

### 2018-04-05 Paper/sense.tex
..

@@
 
-\noindent The derivative-based sensitivity measure, $\mu_i$ for a given parameter, $\theta_i$ is defined as an expectation
+\noindent The derivative-based sensitivity measure, $\mu_i$ for a given parameter, $\theta_i$ is
+defined as an expectation
 of the derivative of the observable ($G(\bm{\theta})$) with respect to that parameter:
@@
 with reasonable accuracy either analytically or numerically. 
- In this work, we examine the suitability of this
-approach based on DGSM for the present application involving thermal transport in bulk Si. We define a 
-normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:
+We define a normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:
 
@@
 \noindent The choice of $\mathcal{C}_i$ is specific to the marginal probability distribution of the uncertain model
-parameter, $\theta_i$. In this work, we consider all uncertain parameters to be uniformly
-distributed in the interval~$[a,b]$ in which case $\mathcal{C}_i$  is given as $(b-a)^{2}/\pi^2$~\cite{Roustant:2014}.
+parameter, $\theta_i$. 
+%We consider all uncertain parameters to be uniformly
+%distributed in the interval~$[a,b]$ in which case $\mathcal{C}_i$  is given as $(b-a)^{2}/\pi^2$~\cite{Roustant:2014}.
+The underlying methodology for implementing DGSM to the present application involving thermal transport in bulk Si,
+and our key findings are presented in the following section.
+
+\subsection{DGSM for SW potential parameters}
+\label{sub:dgsm}
+
+We aim to compute the derivate-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
+Sobol total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
+introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
+associated with each parameter and estimate the partial derivatives in Eq.~\ref{eq:mu} using finite difference. 
+Hence, in order to compute $\mu_i$ using $N$ points in the d-dimensional parameter space, we require $N(d+1)$
+model realizations. The SW potential parameters are considered to be uniformly distributed in a small interval
+around the nominal value in which case $\mathcal{C}_i$ is given as $(u-l)^{2}/\pi^2$~\cite{Roustant:2014}; $u$
+and $l$ being the upper and lower bounds of the interval respectively.
+
+Performing NEMD simulations using perturbed values of the SW potential parameters could however be challenging.
+For certain combinations of the SW potential parameter values, the steady-state thermal
+energy exchange between the thermostats is found to be non-physical at the end of the simulation. We believe that
+this happened in situations where the structure had deviated too far from the equilibrium state and hence the
+structural integrity of the bar is lost as illustrated in Figure~\ref{fig:dgsm1}(a). To avoid this
+issue, we added an NPT ensemble prior to NVT in the NEMD simulation as shown in the following diagram:
+
+\begin{center}
+
+NPT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVT \hspace{5mm} $\rightarrow$ \hspace{5mm} NVE \hspace{5mm}
+$\rightarrow$ \hspace{5mm} NVE
+\\ \vspace{1mm}
+\tiny [Relax the system]~[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+ [Generate Data]
+\\ \vspace{1mm}
+
+\tiny{N: Number of Atoms~~~P: Pressure~~~V: Volume~~~T: Temperature~~~E: Energy}
+\end{center}
+
+\noindent The NPT stage of the simulation was allowed to continue for a sufficiently long duration to ensure
+that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).

### 2018-04-05 Paper/setup.tex
..

@@
 The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}. The set of
-inputs to LAMMPS is provided below in Table~1. Note that specific values for the length of the bar
+inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar
 and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
@@
 \\ \vspace{1mm}
-\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+\tiny \hspace{-5mm}[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
  [Generate Data]

### 2018-04-06 Paper/sense.tex
...

@@
 that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).
+The following algorithm provides the sequence of steps that were used to obtain approximate estimates of the
+sensitivity measures for the SW potential parameters:
+\bigskip
+
+\texttt{Algorithm}
+
+\begin{algorithm}[H]
+\SetAlgoLined
+%\nonl \scriptsize{\textsc{Part I: Parameter Screening}}
+%\nonl \textbf{\texttt{Algorithm}}\;
+\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$}\;
+\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points}
+\texttt{\color{blue} $\%$~$d$: Number of parameters in the SW potential i.e. 7}\;
+\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}}\;
+\texttt{Determine initial ranks, $\mathcal{R}^{old}$ of the parameters based on $\hat{\mathcal{C}_i\mu_i}$ values}\;
+\texttt{set $k$ = 1}
+\texttt{\color{blue}$\%$~$k$:~Iteration counter}\;
+\Repeat{\texttt{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
+$max\_pdev$~$>\tau$)~\color{blue}$\%$~$\tau$:~Tolerance}}{
+\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$}\;
+\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points}\;
+\texttt{Compute and store model evaluations at the $n_k(d+1)$ points}\;
+\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points}\;
+\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values}\;
+\texttt{Compute $max\_pdev$ = max($\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}$)}
+\texttt{\color{blue}$\%$~$max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
+\texttt{set $k$ = $k$ + 1}\;
+}
+\end{algorithm}
+
+For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
+at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
+provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivates in
+Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
+pertaining to the estimation of DGSM can be substantial it is nevertheless several orders of magnitude smaller
+than directly estimating the Sobol indices as mentioned earlier. 
+In Figure~\ref{fig:screen}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
+end of 4 iterations. It appears that $\gamma$ is significantly more important that the rest, whereas NEMD
+predictions are not so sensitive to $B$ and $p$. Large sensitivity towards $\gamma$ and $\alpha$ (cut-off radius)
+ is in fact expected since  these two parameters impact the lattice constant directly.

### 2018-04-07 Paper/ros.tex
...

@@
 \label{sec:ros}
+
+In this section, we focus our attention on constructing a surrogate that captures the dependence of
+uncertainty in NEMD predictions for the bulk thermal conductivity ($\kappa$) on input variability
+in the SW potential parameters. The surrogate is a powerful tool that greatly minimizes
+the computational
+effort required for forward propagation of the uncertainty from input parameters to the observable,
+Sobol sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
+we use polynomial chaos (used to construct response surfaces for discrepancy in
+Section~\ref{sec:response}) to construct the surrogate of the following functional form:
+
+\be
+\kappa  = \sum\limits_{\bm{s}\in\mathcal{A}} c_{\bm{s}}(T)\Psi_{\bm{s}}(\bm{\xi})
+\ee
+
+As discussed earlier in Section~\ref{sec:response}, several strategies are available to
+estimate the PC coefficients, $c_{\bm{s}}$. However, since the polynomial basis functions
+($\Psi_{\bm{s}}(\bm{\xi}$)) are
+relatively high dimensional, we use a computationally efficient approach proposed by
+Blatman and Sudret to construct a PCE with sparse basis($\mathcal{A}$) using the LAR
+algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
+estimating the PC coefficients in the 7D parameter space would still require large amount of
+computational resources. Hence, we explore the possibility of reducing the dimensionality of
+the surrogate. For this purpose, we 
+exploit our observations in Figure~\ref{fig:ub} where a signifcant
+jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and therby construct the 
+PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
+equation, $\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$ is a set
+of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1]. 
+For the five uniformly distributed SW parameters, the prior intervals are considered to be
+$\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
+Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
+($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010} as defined
+below in Eq.~\ref{eq:loo} against the number of model realizations used to construct the 5D
+PC surrogate.
+
+\be
+\epsilon_{\tiny{\mbox{LOO}}} = \frac{\sum\limits_{i=1}^{N}\left(\mathcal{M}(\bm{x}^{(i)}) - 
+\mathcal{M}^{PCE\setminus i}(\bm{x}^{(i)})\right)^{2}}{\sum\limits_{i=1}^{N}
+\left(\mathcal{M}(\bm{x}^{(i)}) - \hat{\mu}_Y\right)^2}
+\label{eq:loo}
+\ee
+
+\noindent where $N$ denotes the number of realizations, $\mathcal{M}(\bm{x}^{(i)})$ is the
+model realization and $\mathcal{M}^{PCE\setminus i}(\bm{x}^{(i)})$ is the corresponding PCE estimate
+at $\bm{x}^{(i)}$. Note that the PCE is constructed using all points except $\bm{x}^{(i)}$.
+The quantity, $\hat{\mu}_Y$ = $\frac{1}{N}\sum\limits_{i=1}^{N}\mathcal{M}(\bm{x}^{(i)})$
+is the sample mean of the realizations. 
+It is found that in order for the PCE to converge to an accuracy of~$\mathcal{O}(10^{-2})$
+with respect to $\epsilon_{\tiny{\mbox{LOO}}}$, we require approximately 160 NEMD runs. In the
+following section, we focus on verifying the accuracy of the 5D PCE against the set of available
+NEMD predictions in the original 7D parameter space.

### 2018-04-07 Paper/sense.tex
...

--- 2018-04-05 Paper/sense.tex
@@
 that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).
+The following algorithm provides the sequence of steps that were used to obtain approximate estimates of the
+sensitivity measures for the SW potential parameters. Note that the algorithm has been adapted to the 
+specific application in this work. A generalized methodology with a more detailed discussion and its application
+to different class of problems will be presented in~\cite{Vohra:2018}.
+
+\bigskip
+
+\begin{breakablealgorithm}
+  \caption{Estimating parameter ranks using DGSM.}
+  \begin{algorithmic}[1]
+    \Procedure{DGSM}{}
+      \State Generate $n_1$ points in $\mathbb{R}^{d}$.\Comment{$d$: 
+             Number of parameters i.e. 7 in this case}
+      \State Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.
+      \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
+      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values.
+      \State set $k$ = 1\Comment{Iteration counter}
+      \Do
+        \State Generate $n_k$ new points in $\mathbb{R}^{d}$.
+        \State Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.
+        \State Compute and store model evaluations at the $n_k(d+1)$ points.
+        \State Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.
+        \State Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values.
+        \State Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - 
+               \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.\Comment{$max\_pdev$:
+               Maximum percentage deviation in $\mu_i$ between successive iterations.}
+        \State set $k$ = $k$ + 1
+      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
+               $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
+    \EndProcedure
+  \end{algorithmic}
+\end{breakablealgorithm}
+
+\bigskip
+
+%\texttt{Algorithm}
+%
+%\begin{algorithm}[H]
+%\SetAlgoLined
+%%\nonl \scriptsize{\textsc{Part I: Parameter Screening}}
+%%\nonl \textbf{\texttt{Algorithm}}\;
+%\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$}\;
+%\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points}
+%\texttt{\color{blue} $\%$~$d$: Number of parameters in the SW potential i.e. 7}\;
+%\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}}\;
+%\texttt{Determine initial ranks, $\mathcal{R}^{old}$ of the parameters based on $\hat{\mathcal{C}_i\mu_i}$ values}\;
+%\texttt{set $k$ = 1}
+%\texttt{\color{blue}$\%$~$k$:~Iteration counter}\;
+%\Repeat{\texttt{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
+%$max\_pdev$~$>\tau$)~\color{blue}$\%$~$\tau$:~Tolerance}}{
+%\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$}\;
+%\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points}\;
+%\texttt{Compute and store model evaluations at the $n_k(d+1)$ points}\;
+%\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points}\;
+%\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values}\;
+%\texttt{Compute $max\_pdev$ = max($\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}$)}
+%\texttt{\color{blue}$\%$~$max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
+%\texttt{set $k$ = $k$ + 1}\;
+%}
+%\end{algorithm}
+
+For the present application, we begin with $n_1$ = 10 samples in the 7D parameter space and add 5 points
+at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
+provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivates in
+Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
+pertaining to the estimation of DGSM can be substantial, it is nevertheless several orders of magnitude smaller
+than directly estimating the Sobol indices as mentioned earlier. 
+In Figure~\ref{fig:ub}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
+end of 4 iterations. It appears that $\gamma$ is significantly more important than other parameters, whereas NEMD
+predictions are relatively less sensitive to $B$ and $p$. Large sensitivity towards 
+$\gamma$ and $\alpha$ (cut-off radius) is in fact expected since  these two parameters impact the lattice
+constant and hence the mean free path associated with the bulk thermal conductivity directly.
+
+In the following section, we exploit these observations based on DGSM to construct a reduced order surrogate.
+The surrogate enables forward propagation of uncertainty in the SW potential to the bulk thermal conductivity 
+estimates, and the estimation of Sobol sensitivity indices with minimal computational effort.

### 2018-04-09 Paper/bayes.tex
...

\section{Bayesian Calibration}
\label{sec:bayes}

As discussed earlier in Section~\ref{sec:intro}, the underlying methodology for determining the nominal 
estimates for SW potential parameters did not account for measurement error, inadequate functional
form of the potential, inherent noise in MD predictions, and parametric uncertainties. Hence, there is
a possibility of improving the estimates since using the same set of values for a wide variety of systems
and applications is not ideal. A robust approach to calibrating the parameters in the presence of
such uncertainties is made possible by using a Bayesian framework. The methodology aims at evaluating
the so-called joint posterior probability distribution (referred to as the `posterior') of the uncertain model 
parameters to be calibrated, using the Bayes' rule:

\be
\mathcal{P}(\bm{X}\vert \bm{Y}) \propto \mathcal{P}(\bm{Y}\vert\bm{X})\mathcal{P}(\bm{X})
\ee

\noindent where $\bm{X}$ is the set of uncertain model parameters, and $\bm{Y}$ is the available set of
experimental data i.e. bulk thermal conductivity at different temperatures in the present case. 
We exploit our findings based on sensitivity analysis in
Figure~\ref{fig:gsa} and focus on calibrating $\alpha$ and $\gamma$ i.e. $\bm{X}:\{\alpha,\gamma\}$.
$\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
`likelihood', and $\mathcal{P}(\bm{X})$ is the prior probability distribution (referred to as the `prior') of $\bm{X}$.
The likelihood accounts for measurement error, and the discrepancy between experiments and model
predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
interval. It also accounts for the availability of an expert opinion pertaining to their estimates. 
The posterior provides an estimate of the most likely value of the uncertain model parameters based on
prior uncertainty, experimental data used for calibration and the associated measurement error, and model
discrepancy. Additionally, the posterior is often used to quantify the uncertainty associated with model predictions. Several algorithms based on Markov chain Monte Carlo (MCMC) technique are available for  
sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.

Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
computational effort and is not the focus on this work. Instead, we compute and plot the joint likelihood on
a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
Figure~\ref{fig:like}(a). For this purpose, we consider $\alpha$ and $\gamma$ to be
independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
Consequently, the joint posterior is proportional to the likelihood, considered to be a Gaussian:

\be
\mathcal{P}(\bm{Y}\vert\bm{X}) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left[-\frac{(\kappa_{\tiny{\mbox{E}}} - 
\kappa_{\tiny{\mbox{MD}}})^2}{2\sigma^2}\right]
\label{eq:like}
\ee

\noindent where $\sigma$ is the standard deviation of the measurement error, and
$(\kappa_{\tiny{\mbox{E}}} - \kappa_{\tiny{\mbox{MD}}})$ is the discrepancy between 
NEMD predictions~($\kappa_{\tiny{\mbox{MD}}}$)
and experimental data~($\kappa_{\tiny{\mbox{E}}}$). Experimental data for $\kappa_{\tiny{\mbox{E}}}$ at 300~K
(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood. Marginal distributions for
$\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
should be evaluated using a substantially large set of experimental data and surrogates for NEMD predictions
need to be constructed (as discussed in Section~\ref{sec:ros}) for each temperature to reduce computational effort. 
The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using
Sobol sensitivity analysis as presented in this work.

### 2018-04-09 Paper/ros.tex
...

@@
 below in Eq.~\ref{eq:loo} against the number of model realizations used to construct the 5D
-PC surrogate.
+PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
+the surrogate.
 
@@
 NEMD predictions in the original 7D parameter space.
+
+\subsection{PC Surrogate Verification}
+
+The accuracy of the 5D PC surrogate is verified using two different strategies. The first strategy involves
+computing the relative L-2 norm of the difference between the available NEMD predictions (used earlier
+to estimate DGSM in Section~\ref{sec:sense}) and estimates using the 5D surrogate as follows:
+
+\be
+\epsilon_{\mbox{\tiny{L-2}}} = 
+\frac{\left[\sum\limits_{i=1}^{N=25}\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)}) - 
+\mathcal{M}^{PCE}(\bm{\theta}_{\mbox{\tiny{5D}}}^{(i)})\right)^{2}\right]^{\frac{1}{2}}}{\left[\sum_{i=1}^{N}
+\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)})\right)^2\right]^{\frac{1}{2}}} \approx 6.88\times 10^{-2}
+\ee
+
+\noindent Since $\epsilon_{\mbox{\tiny{L-2}}}$ is found to be $\mathcal{O}(10^{-2})$, the 5D surrogate can be considered as
+reasonably accurate from the perspective of relative L-2 error norm.
+
+In the second strategy, we compare NEMD
+predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
+histogram plot based on the available set of NEMD predictions in the 7D parameter space is compared with
+the bulk thermal conductivity distribution as obtained using the reduced order surrogate and 10$^6$ samples in the
+5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$. It is
+observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
+favorably with the histogram plot. Specifically, the corresponding mode values for $\kappa$ from the two plots are
+in close agreement, the PDF reasonably captures the peaks observed in the histogram, as well as the spread in
+the bulk thermal conductivity distribution. 
+Hence, the reduced order surrogate is verified for accuracy in both cases. 
+\bigskip
+
+As mentioned earlier, a PC surrogate can be used to estimate Sobol global sensitivity indices in a 
+straightforward manner~\cite{Sudret:2008}. Sobol first order and total effect sensitivity indices as estimated
+using the reduced order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
+Figure~\ref{fig:gsa}. It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
+$\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D
+parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
+While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, Sobol
+indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
+for $\alpha$ and $\gamma$. Large quantitative disagreements in parametric sensitivity between DGSM and the 
+Sobol indices is however not unexpected essentially because they differ by construction. The former is based
+on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
+agreements pertaining to parameter importance in the two approaches is quite encouraging. 
+Moreover, verification of the reduced order
+surrogate for accuracy increases our confidence in implementing DGSM to ascertain relative importance of the
+SW potential parameters and hence perform uncertainty analysis for the present application with minimal
+computational effort.

### 2018-04-09 Paper/ack.tex
...

\section*{Acknowledgment}
\label{sec:ack}

M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
National Science Foundation Award $\#$. Molecular
dynamics simulations were performed using resources at the advanced computing
center for research and education (ACCRE) at Vanderbilt University. 
M. Vohra is grateful to the ACCRE staff for their technical guidance
and support. He would also like to sincerely thank Dr. Alen Alexanderian for
insightful discussions pertaining to the derivative-based sensitivity analysis
aspect of this work.

### 2018-04-09 Paper/bayes.tex
...

@@
 and experimental data~($\kappa_{\tiny{\mbox{E}}}$). Experimental data for $\kappa_{\tiny{\mbox{E}}}$ at 300~K
-(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood. Marginal distributions for
+(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/gl}
+  \\ (a)
+  \begin{tabular}{cc}
+  \includegraphics[width=0.50\textwidth]{./Figures/pdf_alpha}
+  &
+  %\hspace{3mm}
+  \includegraphics[width=0.50\textwidth]{./Figures/pdf_gamma}
+  \\ (b) & (c)
+  \end{tabular}
+\caption{(a) A joint likelihood as estimated using Eq.~\ref{eq:like} is plotted on a 2D cartesian grid
+ ($\alpha\times\gamma$). Point corresponding to the maximum likelihood (MLE) is also highlighted.
+ The likelihood is plotted along a line passing through MLE and parallel to the $\alpha$-axis
+ in (b), and $\gamma$-axis in (c).}
+\label{fig:like}
+\end{center}
+\end{figure}
+
+Approximate marginal distributions for
 $\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 

### 2018-04-09 Paper/disc.tex
...

\section{Summary and Discussion}
\label{sec:disc}

In this paper, we have attempted to identify and address some of the challenges
pertaining to uncertainty analysis of bulk thermal conductivity predictions 
using non-equilibrium molecular dynamics (NEMD) simulations. Specifically, we focused
on investigating the impact of system size, and variability in the applied thermal
gradient on predictions. In order to quantify the discrepancy between NEMD
predictions and experiments, response surfaces were  
constructed at bulk temperatures, $T$ = 300~K, 500~K, and 1000~K.  
It was found that the discrepancy is predominantly impacted by size while the 
effect of variability in the applied thermal gradient is negligible in the considered
interval. The response surface approach presented here relies on a small number of
MD runs and enables an accurate estimation of discrepancy at a given temperature
and a point in the 2D parameter space described by system-size and the applied
thermal gradient.

A possible enhancement of nominal SW parameter estimates for a given application
and the choice of material system is also highlighted in this work. To enable this,
we focus our efforts on understanding the sensitivity of predictions on the 
parameters. For this purpose, we estimate the so-called derivative based sensitivity
measures (DGSM) using random samples in the 7D parameter space. While individual
measures for the 7 parameters are not too distant from each other, the predictions
seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
$\lambda$, $q$, and $A$ are found to be comparable while those for $B$ and $p$
are relatively small.

A polynomial chaos surrogate model for the bulk thermal conductivity (observable)
as a function of SW potential
parameters at a given temperature is constructed. The surrogate helps reduce the
computational effort required for forward propagation of the uncertainty from
parameters to the observable as well as for estimating the Sobol sensitivity indices.
Furthermore, the surrogate could be used to accelerate parameter calibration in a
Bayesian setting. However, since the surrogate relies on NEMD predictions, the
underlying computational effort is nevertheless significantly large. To circumvent
this challenge, we exploit our initial findings based on DGSM and construct
a reduced order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
We verify its accuracy by estimating the relative
L-2 norm of the error between NEMD predictions in the full space and the reduced
order surrogate predictions, and comparing the probability distribution of the
bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
sensitivity trends based on DGSM-analysis using 25 samples seems to agree favorably
with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
that DGSM-based analysis with a few samples could offer huge computational gains
by reliably reducing the dimensionality of a surrogate for uncertainty analysis.

Finally, we highlight key aspects of parameter calibration in a Bayesian setting.
The underlying motivation stems from the fact that the nominal estimates of the SW
parameters did not consider measurement error, simulation noise, model form error,
and parametric uncertainties. Calibration in a Bayesian framework allows us to
incorporate such errors and uncertainties in an efficient manner and provides
a joint posterior distribution of the uncertain parameters. To minimize computational
costs pertaining to the calibration process, we suggest the following sequence of
steps: First, perform DGSM analysis to 
identify parameter that are not so important. Second, construct a reduced order
surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate
and compute Sobol indices. Fourth, consider only the important parameters in
calibration and construct a second surrogate in the reduced subspace. Fifth,
quantify the surrogate error to be accounted for during calibration. Sixth,
evaluate the joint posterior using an efficient MCMC-based algorithm.

In conclusion, the authors would like to highlight that the strategies presented 
in this work are not restricted to a Si bar and the Stillinger-Weber potential, and
could be extended to a wide range of applications and inter-atomic potentials for
the purpose of uncertainty analysis.

### 2018-04-09 Paper/intro.tex
...

@@
 (cite Amuthan book, Francesco's paper, McGaughey's paper). 
-Errors are introduced by thermostatting (Amuthan book). Nominal value of SW potential parameters based on fitting against experiments and to ensure structural stability etc. (SW paper)
+Errors are introduced by thermostatting (Amuthan book). Nominal value of SW potential parameters
+based on fitting against experiments and to ensure structural stability etc. (SW paper)
 
@@
 technique that involves the application
-of a heat flux or a temperature gradient by means of thermostatting across the system. 
+of a heat flux or a temperature gradient by means of thermostatting, across the system. 
 Corresponding steady-state temperature gradient in the former or the heat exchange between
-the two thermostats in the latter, is used to estimate thermal conductivity (at a given
+the two thermostats in the latter, is used to estimate the bulk thermal conductivity (at a given
 length or size) using 
@@
 the thermal conductivity
-further~\cite{Evans:2008}. Estimate of thermal conductivity using the
+further~\cite{Evans:2008}. Estimation of thermal conductivity using the
 direct method is therefore impacted by the choice of system size and potentially due to
-variability in the thermal gradient experienced by the system owing to
-Kapitza effect.
+variability in the thermal gradient experienced by the system due to thermostatting.
 
-Predictions of non-equilibrium molecular dynamics (NEMD) simulations are dependent on the
+Predictions of non-equilibrium molecular dynamics (NEMD) simulations are also dependent on the
 choice of the inter-atomic potential as well as values associated with individual parameters
@@
 is a widely used inter-atomic potential. However, as discussed by Stillinger and Weber
-in~\cite{Stillinger:1985}, the proposed nominal values of individual parameters were based
+in~\cite{Stillinger:1985}, the proposed nominal values of individual parameters are based
 on a limited search in the 7D parameter space while ensuring structural stability and
@@
 wide variety of Si-based systems and warrant further investigation to study the impact of
-underlying uncertainties on MD predictions. 
-In a recent effort, Rizzi et al. study the effect of
+underlying uncertainties on MD predictions. Along these lines, 
+a recent study by Rizzi et al. focused on the effect of
 uncertainties associated with the force-field parameters on bulk water properties using MD
-simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} consider a stochastic model
-for thermal conductivity (due to noise in MD simulations) and study its impact on spatial temperature 
+simulations~\cite{Rizzi:2012}. Marepalli et al. in~\cite{Marepalli:2014} considered a stochastic model
+for thermal conductivity to account for inherent noise in MD simulations, and study its impact on
+spatial temperature 
 distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implement an uncertainty
@@
 variability in predictions~(Section~\ref{sec:sense}).
-Third, we exploit our findings from sensitivity analysis to discern important parameters and hence
-reduce the dimensionality of the problem~(Section~\ref{sec:ros}). Fourth, we illustrate calibration
+Third, we exploit our findings from sensitivity analysis to 
+construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
+Fourth, we illustrate calibration
 of the important parameters in a Bayesian setting to evaluate their posterior
@@
 challenging endeavors especially in situations involving compute-intensive simulations as in the
-case of NEMD. We therefore employ polynomial choas (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
+case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
 using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce computational effort pertaining

### 2018-04-09 Paper/ros.tex
...

@@
 the surrogate. For this purpose, we 
-exploit our observations in Figure~\ref{fig:ub} where a signifcant
-jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and therby construct the 
+exploit our observations in Figure~\ref{fig:ub} where a significant
+jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
 PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
@@
 of five canonical random variables, $\xi_i$ distributed uniformly in the interval [-1,1].
-For the five uniformly distributed SW parameters, the prior intervals are considered to be
+Prior intervals for the uncertain SW parameters are considered to be
 $\pm~10\%$ of their respective nominal estimates except for $q$ in which case it is [0,0.1]. In
@@
 is the sample mean of the realizations.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_eloo}
+\caption{A convergence study for the 5D PCE wherein the leave-one-out
+error, $\epsilon_{\tiny{\mbox{LOO}}}$ is plotted against the number of
+realizations or NEMD runs used to estimate the PC coefficients.}
+\label{fig:loo}
+\end{center}
+\end{figure}
+
 It is found that in order for the PCE to converge to an accuracy of~$\mathcal{O}(10^{-2})$
@@
 the bulk thermal conductivity distribution as obtained using the reduced order surrogate and 10$^6$ samples in the
-5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$. It is
-observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
+5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_kde}
+\caption{Comparison of bulk thermal conductivity ($\kappa$) distribution of Si based on a histogram plot
+using NEMD predictions (Model) at 25 points in the 7D parameter space and a probability distribution obtained 
+using kernel density estimation of  reduced order surrogate estimates of $\kappa$ for 10$^6$ samples in the 5D
+parameter space.}
+\label{fig:verify}
+\end{center}
+\end{figure}
+
+It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
 favorably with the histogram plot. Specifically, the corresponding mode values for $\kappa$ from the two plots are
@@
 using the reduced order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
-Figure~\ref{fig:gsa}. It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
+Figure~\ref{fig:gsa}.
+
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_gsa}
+\caption{Sobol first-order and total effect sensitivity indices as obtained using the reduced order PC
+surrogate and 10$^{6}$ samples in the 5D parameter space. }
+\label{fig:gsa}
+\end{center}
+\end{figure}
+
+It is found that $\kappa$ is predominantly sensitive towards the choice of $\alpha$ and
 $\gamma$. This observation is consistent with our initial findings based on DGSM using 25 samples in the 7D

### 2018-04-09 Paper/sense.tex
...

@@
 converge to the upper bound on
-Sobol index with only a few iterations~($\mathcal{O}(10^{1})$) thereby leading to enormous computational savings. 
+Sobol index with only a few iterations~($\mathcal{O}(10^{1})$). 
 In that case, estimates of the upper bound could be used in lieu of the
-Sobol indices to determine relative importance of the parameters. The upper bound on 
+Sobol indices to determine relative importance of the parameters and hence reduce the associated computational
+effort by several order of magnitude. The upper bound on 
 Sobol total effect index\footnote{Sobol total effect index is a measure of the contribution of a 
@@
 constant~($\mathcal{C}_i$), and the total variance of the observed
-quantity~($V$)~\cite{Lamboni:2013,Roustant:2014}:
+quantity~($V$)~\cite{Lamboni:2013,Roustant:2014} as follows:
 
@@
 exhibit a smooth variation with each parameter so that the derivative in Eq.~\ref{eq:mu} can be estimated
-with reasonable accuracy either analytically or numerically. 
+with reasonable accuracy, analytically or numerically. 
 We define a normalized quantity, $\hat{\mathcal{C}_i\mu_i}$ to ensure that its summation over all parameters is 1:
@@
 The underlying methodology for implementing DGSM to the present application involving thermal transport in bulk Si,
-and our key findings are presented in the following section.
+and our key findings are discussed in the following section.
 
@@
 
-We aim to compute the derivate-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
+We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
 Sobol total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
@@
 For certain combinations of the SW potential parameter values, the steady-state thermal
-energy exchange between the thermostats is found to be non-physical at the end of the simulation. We believe that
-this happened in situations where the structure had deviated too far from the equilibrium state and hence the
-structural integrity of the bar is lost as illustrated in Figure~\ref{fig:dgsm1}(a). To avoid this
-issue, we added an NPT ensemble prior to NVT in the NEMD simulation as shown in the following diagram:
+energy exchange between the thermostats was found to be non-physical at the end of the simulation. We believe that
+this was observed in situations 
+where the structure had deviated too far from the equilibrium state, and therefore the
+structural integrity of the bar was lost as illustrated in Figure~\ref{fig:dgsm1}(a).
+
+\begin{figure}[htbp]
+\begin{center}
+\begin{tabular}{cc}
+  \includegraphics[width=0.40\textwidth]{./Figures/unstable}
+  &
+  \hspace{3mm}
+  \includegraphics[width=0.50\textwidth]{./Figures/lx_npt}
+  \\ (a) & (b)
+  \end{tabular}
+\caption{(a) A snapshot of the arrangement of atoms illustrating loss of
+structural integrity of the Si bar. 
+(b) Si bar length is plotted against the number of time steps during
+the NPT ensemble stage of the simulation.}
+\label{fig:dgsm1}
+\end{center}
+\end{figure}
+
+To avoid this issue, we added an NPT ensemble prior to NVT in the NEMD simulation as shown in the
+following diagram:
 
@@
 that the system is relaxed to a steady value of the bar length as shown in Figure~\ref{fig:dgsm1}(b).
+
 The following algorithm provides the sequence of steps that were used to obtain approximate estimates of the
@@
       \State Compute $\mu_i$ using model evaluations at the $n_1(d+1)$ points in Eq.~\ref{eq:mu}
-      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values.
+      \State Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values for $\theta_i$.
       \State set $k$ = 1\Comment{Iteration counter}
@@
         \State set $k$ = $k$ + 1
-      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ $\&$ 
+      \doWhile{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
                $max\_pdev$~$>~\tau$)\Comment{$\tau$:~Tolerance}}
@@
 at each iteration. Using a tolerance, $\tau$ = 0.05, the above algorithm took 4 iterations i.e. 25 points to 
-provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivates in
+provide approximate estimates for $\mu_i$. Since finite difference was used to estimate the derivatives in
 Eq.~\ref{eq:mu}, it required 25(7+1) i.e. 200 MD runs. It must be noted that although the computational effort
@@
 
+\begin{figure}[htbp]
+ \begin{center}
+  \includegraphics[width=0.70\textwidth]{./Figures/ub}
+\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 25(7+1)
+points is plotted for each SW potential parameter.}
+\label{fig:ub}
+\end{center}
+\end{figure}
+
 In the following section, we exploit these observations based on DGSM to construct a reduced order surrogate.

### 2018-04-09 Paper/setup.tex
...

@@
 
-Non-equilibrium molecular dynamics (NEMD) simulations are performed in LAMMPS~\cite{Plimpton:2007}
-by applying a thermal gradient by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$. 
-The atomic configuration as well as a schematic of the set-up is provided in Figure~\ref{fig:setup}. The set of
+Non-equilibrium molecular dynamics (NEMD) simulations are performed using LAMMPS~\cite{Plimpton:2007}.
+Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
+as shown using a schematic in Figure~\ref{fig:setup}.
+
+\begin{figure}[htbp]
+\begin{center}
+\begin{tabular}{cc}
+  \includegraphics[width=0.48\textwidth]{./Figures/schematic}
+  &
+  \hspace{3mm}
+  \includegraphics[width=0.40\textwidth]{./Figures/Sibar_05}
+  \\ (a) & (b)
+  \end{tabular}
+\caption{(a) Schematic illustration of the set-up for evaluating thermal conductivity of Si using NEMD. (b) 
+Arrangement of Si atoms prior to the application of thermal gradient.}
+\label{fig:setup}
+\end{center}
+\end{figure}
+
+The set of
 inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar

### 2018-04-10 Slides/r1/md_si.tex
..

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  This Beamer template was created by Cameron Bracken.
%%  Anyone can freely use or modify it for any purpose
%%  without attribution.
%%
%%  Last Modified: January 9, 2009
%%

\documentclass[xcolor={x11names,table},compress,svgnames,mathserif]{beamer}

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
%\usepackage{lmodern}
\usepackage{animate}
\usepackage{movie15}
\usepackage{bm}
\usepackage{pifont}
\usepackage{empheq}
\usepackage[many]{tcolorbox}
\usepackage{smartdiagram}
\usepackage[customcolors]{hf-tikz}
\usepackage{dashrule} % for dotted vertical line
%\usepackage{flexisym}

\usepackage[absolute,overlay]{textpos}

\pgfdeclarehorizontalshading{section shading}{2cm}{
color(0cm)=(LightSlateGrey);
color(2cm)=(gray!7);
color(3cm)=(LightSlateGrey!15)
}

% Custom block environment
% Custom block environment
\newenvironment<>{varblock}[2][.9\textwidth]{%
  \setlength{\textwidth}{#1}
  \begin{actionenv}#3%
    \def\insertblocktitle{#2}%
    \par%
    \usebeamertemplate{block begin}}
  {\par%
    \usebeamertemplate{block end}%
  \end{actionenv}}

% boxed equaton
\usepackage[many]{tcolorbox}
%\tcbuselibrary{skins}

\tcbset{highlight math style={enhanced,
  colframe=red!60!black,colback=yellow!50!white,arc=4pt,boxrule=1pt,
  }}

\newtcbox{\mybox}[1][]{nobeforeafter,math upper,tcbox raise base,
  enhanced,frame hidden,boxrule=0pt,interior style={top color=green!10!white,
  bottom color=green!10!white,middle color=green!50!yellow},
  fuzzy halo=1pt with green,drop large lifted shadow,#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning,decorations.pathreplacing}
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=purple!20, 
    text width=5.0em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw=none, fill=blue!20, anchor=north, 
    text width=9.0em, text centered]
    \tikzstyle{blockr} = [rectangle, draw, fill=blue!20, 
    text width=9.0em, text centered, rounded corners]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw=none, ellipse,fill=purple!20, node distance=3cm,
    minimum height=2em]

%% Beamer Layout %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\useoutertheme[subsection=false,shadow]{miniframes}
\useinnertheme{default}
%\usefonttheme{serif}
\usepackage{palatino}
\usepackage{xcolor}
\usepackage{amsmath}
\newcommand{\angstrom}{\textup{\AA}}

\setbeamerfont{title like}{shape=\scshape}
\setbeamerfont{frametitle}{shape=\scshape}
\setbeamertemplate{itemize items}[triangle] % if you wnat a circle
\setbeamertemplate{itemize subitem}[triangle]
\setbeamertemplate{navigation symbols}{}
%\setbeamertemplate{footline}[frame number]

\setbeamercolor{footlinecolor}{fg=white,bg=DeepSkyBlue4}
\defbeamertemplate*{footline}{infolines theme}
{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{footlinecolor}
 % {author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshortauthor
   % \usebeamerfont{author in head/foot}\insertshortauthor~~(\insertshortinstitute)
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,center]{title in head/foot}%
    \usebeamerfont{title in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.333333\paperwidth,ht=2.25ex,dp=1ex,right]{footlinecolor}
  %{date in head/foot}%
   % \usebeamerfont{date in head/foot}\insertshortdate{}\hspace*{2em}
    \usebeamerfont{date in head/foot}{manav.vohra@vanderbilt.edu}\hspace*{2em}
    \insertframenumber{} / \inserttotalframenumber\hspace*{2ex} 
  \end{beamercolorbox}}%
  \vskip0pt%
}
%\setbeamercolor{section in head/foot}{fg=white, bg=DeepSkyBlue4}

\setbeamercolor*{lower separation line head}{bg=DeepSkyBlue4} 
\setbeamercolor*{normal text}{fg=black,bg=white} 
\setbeamercolor*{alerted text}{fg=red} 
\setbeamercolor*{example text}{fg=black} 
\setbeamercolor*{structure}{fg=black}

\setbeamercolor*{palette tertiary}{fg=black,bg=black!10} 
\setbeamercolor*{palette quaternary}{fg=black,bg=black!10}

\renewcommand{\(}{\begin{columns}}
\renewcommand*\footnoterule{}
\renewcommand{\)}{\end{columns}}
\newcommand{\<}[1]{\begin{column}{#1}}
\renewcommand{\>}{\end{column}}

\newcommand*\subitem{%
  \item[\color{DeepSkyBlue4}\scalebox{0.6}{\ding{228}}]}

  \newcommand*\subitemtwo{%
  \item[\color{LightSlateGrey!15}\scalebox{0.6}{\ding{228}}]}

\newcommand*\myitem{%
  \item[\color{DeepSkyBlue4}\scalebox{0.6}{\ding{110}}]}

  \newcommand*\myitemtwo{%
  \item[\color{LightSlateGrey!15}\scalebox{0.6}{\ding{110}}]}

\newcommand*\Myitem{%
  \item[\color{DeepSkyBlue4}\scalebox{0.9}{\ding{42}}]}

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\p}{\partial}
\def\ol{\overline}
\def\no{\noindent}
\def\Vb{{\cal V}}
\def\Qd{\dot{Q}}
%\DeclareMathSymbol{\ast}{\mathbin}{symbols}{"03}
 \newcommand{\argmax}{\operatornamewithlimits{arg\,max}}

%-----------Parameter screening tikz styles -----------------------
   \tikzstyle{A} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=blue!30]
      \tikzstyle{B} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=red!30]
      \tikzstyle{p} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=yellow!30]
      \tikzstyle{q} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=green!30]
      \tikzstyle{alpha} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=magenta!30]
      \tikzstyle{lambda} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=cyan!30]
      \tikzstyle{gamma} = [rectangle, rounded corners, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,
     fill=orange!30]
 \tikzstyle{outer} = [rectangle, minimum width=1.5cm, minimum height=0.5cm,text centered, draw=black,dashed]    
 \tikzstyle{pool} = [rectangle, minimum width=2.0cm, minimum height=1.6cm,line width=1pt,
text centered, draw=black,dashed]

%% Algorithm %%%%%
\usepackage[linesnumbered]{algorithm2e}
\newcommand{\nosemic}{\renewcommand{\@endalgocfline}{\relax}}% Drop semi-colon ;
\newcommand{\dosemic}{\renewcommand{\@endalgocfline}{\algocf@endline}}% Reinstate semi-colon ;
\newcommand{\pushline}{\Indp}% Indent
\newcommand{\popline}{\Indm\dosemic}% Undent
\let\oldnl\nl% Store \nl in \oldnl
\newcommand{\nonl}{\renewcommand{\nl}{\let\nl\oldnl}}% Remove line number for one
\SetKwRepeat{Do}{do}{while}
%%%%%%%%%%%%%%%%%

%---------------------QUOTATION--------------------------
\usepackage{etoolbox}
%\usepackage[svgnames]{xcolor}
\usepackage{framed}

% conditional for xetex or luatex
\newif\ifxetexorluatex
\ifxetex
  \xetexorluatextrue
\else
  \ifluatex
    \xetexorluatextrue
  \else
    \xetexorluatexfalse
  \fi
\fi
%
\ifxetexorluatex%
  \usepackage{fontspec}
  \usepackage{libertine} % or use \setmainfont to choose any font on your system
  \newfontfamily\quotefont[Ligatures=TeX]{Linux Libertine O} % selects Libertine as the quote font
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  %\usepackage{libertine} % or any other font package
  \newcommand*\quotefont{\fontfamily{LinuxLibertineT-LF}} % selects Libertine as the quote font
\fi

\newcommand*\quotesize{30} % if quote size changes, need a way to make shifts relative
% Make commands for the quotes
\newcommand*{\openquote}
   {\tikz[remember picture,overlay,xshift=-3ex,yshift=-0.5ex]
   \node (OQ) {\quotefont\fontsize{\quotesize}{\quotesize}\selectfont``};\kern0pt}

\newcommand*{\closequote}[1]
  {\tikz[remember picture,overlay,xshift=-15ex,yshift={#1}]
   \node (CQ) {\quotefont\fontsize{\quotesize}{\quotesize}\selectfont''};}

% select a colour for the shading
\colorlet{shadecolor}{Azure}

\newcommand*\shadedauthorformat{\emph} % define format for the author argument

% Now a command to allow left, right and centre alignment of the author
\newcommand*\authoralign[1]{%
  \if#1l
    \def\authorfill{}\def\quotefill{\hfill}
  \else
    \if#1r
      \def\authorfill{\hfill}\def\quotefill{}
    \else
      \if#1c
        \gdef\authorfill{\hfill}\def\quotefill{\hfill}
      \else\typeout{Invalid option}
      \fi
    \fi
  \fi}
% wrap everything in its own environment which takes one argument (author) and one optional argument
% specifying the alignment [l, r or c]
%
\newenvironment{shadequote}[2][l]%
{\authoralign{#1}
\ifblank{#2}
   {\def\shadequoteauthor{}\def\yshift{-2ex}\def\quotefill{\hfill}}
   {\def\shadequoteauthor{\par\authorfill\shadedauthorformat{#2}}\def\yshift{2ex}}
\begin{snugshade}\begin{quote}\openquote}
{\shadequoteauthor\quotefill\closequote{\yshift}\end{quote}\end{snugshade}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[UQ: Nano-scale Phonon Heat Transfer]{\textbf{Characterizing Errors and Uncertainties in
NEMD Simulations of Phonon Transport}}
\thispagestyle{empty}
\pgfsetfillopacity{0.9}
\setbeamercolor{title}{bg=DeepSkyBlue4,fg=white}

%\subtitle{SUBTITLE}
\author[M. Vohra and S. Mahadevan]{Manav Vohra$^{\dag}$, Sankaran Mahadevan$^{\dag}$ \\ \vspace{2mm}
\scriptsize{Collaborators: Seungha Shin$^{\S}$, Ali Yousefzadi Nobakht$^{\S}$}}
\vspace{-1mm}
\institute{$^{\dag}$Vanderbilt University\\ \vspace{1mm}
$^{\S}$University of Tennessee, Knoxville}

\date{\today}

\begin{document}

%___________________________NEW SLIDE______________________________________
{
\setbeamertemplate{headline}{}

\begin{frame}[noframenumbering]

\titlepage
\vspace{-21mm}
\centering
%\scriptsize Institute for Computational Engineering and Sciences\\ \vspace{1mm}
%The University of Texas at Austin \\ \vspace{6mm}

%\footnotesize Seminar at SCI, University of Utah \\ \vspace{2mm}

\end{frame}
}

%___________________________NEW SLIDE______________________________________

\end{document}

### 2018-04-10 Slides/origin/gen_slides.sh

@@ -1,0 +1,5 @@
+#!/bin/sh
+
+pdflatex md_si.tex
+pdflatex md_si.tex
+rm *.aux *.log *.out *.toc *.nav *.snm

### 2018-04-10 Paper/bayes.tex
..

@@
 $\mathcal{P}(\bm{X}\vert \bm{Y})$ is regarded as the posterior, $\mathcal{P}(\bm{Y}\vert\bm{X})$ is the
-`likelihood', and $\mathcal{P}(\bm{X})$ is the prior probability distribution (referred to as the `prior') of $\bm{X}$.
+`likelihood', and $\mathcal{P}(\bm{X})$ is the joint prior probability distribution (referred to as the `prior') of $\bm{X}$.
 The likelihood accounts for measurement error, and the discrepancy between experiments and model
@@
 independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
-Consequently, the joint posterior is proportional to the likelihood, considered to be a Gaussian:
+Consequently, the posterior is proportional to the likelihood, considered to be a Gaussian:
 
@@
 It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
-should be evaluated using a substantially large set of experimental data and surrogates for NEMD predictions
-need to be constructed (as discussed in Section~\ref{sec:ros}) for each temperature to reduce computational effort. 
+should be evaluated using a substantially large set of experimental data for bulk thermal conductivity as a function
+of temperature, and surrogates for NEMD predictions
+need to be constructed (as discussed in Section~\ref{sec:ros}) at each temperature for which the data is made
+available in order to reduce computational effort. 
 The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using

### 2018-04-10 Paper/disc.tex
..

@@
 and the choice of material system is also highlighted in this work. To enable this,
-we focus our efforts on understanding the sensitivity of predictions on the 
+we focus our efforts on understanding the sensitivity of predictions on individual potential
 parameters. For this purpose, we estimate the so-called derivative based sensitivity
@@
 as a function of SW potential
-parameters at a given temperature is constructed. The surrogate helps reduce the
+parameters at the bulk temperature of 300~K is constructed. The surrogate helps reduce the
 computational effort required for forward propagation of the uncertainty from
@@
 bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
-sensitivity trends based on DGSM-analysis using 25 samples seems to agree favorably
+sensitivity trends based on DGSM-analysis using 25 samples seem to agree favorably
 with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
@@
 steps: First, perform DGSM analysis to 
-identify parameter that are not so important. Second, construct a reduced order
+identify parameters that are not so important. Second, construct a reduced order
 surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate

### 2018-04-10 Paper/ros.tex
..

@@
 Figure~\ref{fig:loo}, we plot the leave-one-out cross-validation error 
-($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010} as defined
-below in Eq.~\ref{eq:loo} against the number of model realizations used to construct the 5D
+($\epsilon_{\tiny{\mbox{LOO}}}$)~\cite{Blatman:2010}, defined
+below in Eq.~\ref{eq:loo}, against the number of model realizations used to construct the 5D
 PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
@@
 
-\noindent Since $\epsilon_{\mbox{\tiny{L-2}}}$ is found to be $\mathcal{O}(10^{-2})$, the 5D surrogate can be considered as
+\noindent where $\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)})$ is the NEMD prediction in the original 7D
+parameter space, and $\mathcal{M}^{PCE}(\bm{\theta}_{\mbox{\tiny{5D}}}^{(i)})$ is the corresponding 
+estimate using the reduced order surrogate (5D). 
+Since $\epsilon_{\mbox{\tiny{L-2}}}$ is found to be $\mathcal{O}(10^{-2})$, the 5D surrogate can be considered as
 reasonably accurate from the perspective of relative L-2 error norm.
-
-In the second strategy, we compare NEMD
-predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
-histogram plot based on the available set of NEMD predictions in the 7D parameter space is compared with
-the bulk thermal conductivity distribution as obtained using the reduced order surrogate and 10$^6$ samples in the
-5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$.
 
@@
 
+In the second strategy, we compare NEMD
+predictions and estimates from the 5D surrogate in a probabilistic sense. As shown in Figure~\ref{fig:verify}, a 
+histogram plot based on the available set of NEMD predictions for bulk thermal conductivity in the 7D parameter 
+space is compared with its probability distribution, obtained using the reduced order surrogate and
+10$^6$ samples in the 5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$.
 It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
-favorably with the histogram plot. Specifically, the corresponding mode values for $\kappa$ from the two plots are
-in close agreement, the PDF reasonably captures the peaks observed in the histogram, as well as the spread in
-the bulk thermal conductivity distribution. 
+favorably with the histogram. Specifically, the corresponding mode values for $\kappa$ from the two plots are
+in close agreement, and the PDF reasonably captures the peaks as well as the spread in
+the bulk thermal conductivity distribution as observed in the histogram. 
 Hence, the reduced order surrogate is verified for accuracy in both cases. 
@@
 indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
-for $\alpha$ and $\gamma$. Large quantitative disagreements in parametric sensitivity between DGSM and the 
-Sobol indices is however not unexpected essentially because they differ by construction. The former is based
+for $\alpha$ and $\gamma$. Large quantitative disagreement in parametric sensitivity between DGSM and the 
+Sobol indices is however not unexpected essentially because the two metrics differ by construction.
+The former is based
 on an expectation of partial derivatives while the later is based on variance. Nevertheless, significant qualitative
-agreements pertaining to parameter importance in the two approaches is quite encouraging. 
+agreement pertaining to parameter importance in the two approaches is quite encouraging. 
 Moreover, verification of the reduced order

### 2018-04-11 Slides/r1/md_si.tex
..

@@
 \usepackage{dashrule} % for dotted vertical line
+\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\definecolor{pigment}{rgb}{0.2, 0.2, 0.6}
 %\usepackage{flexisym}
@@
 \author[M. Vohra and S. Mahadevan]{Manav Vohra$^{\dag}$, Sankaran Mahadevan$^{\dag}$ \\ \vspace{2mm}
-\scriptsize{Collaborators: Seungha Shin$^{\S}$, Ali Yousefzadi Nobakht$^{\S}$}}
+\scriptsize{Collaborators: Seungha Shin$^{\S}$, Ali Y. Nobakht$^{\S}$}}
 \vspace{-1mm}
@@
 
+\section{\scshape Background}
+\subsection{bg}
+
+\begin{frame}{Non-Equilibrium MD}
+
+\begin{itemize}
+
+\myitem Widely used to study thermal (phonon) transport in 
+{\color{pigment}non-metallic} systems (C,Si,Ge).
+\vspace{2mm}
+\myitem System subjected to a temperature gradient using thermostats.
+\vspace{2mm}
+\myitem {\color{pigment}Steady-state} thermal energy exchange between
+the thermostats is used in Fourier's law to estimate bulk thermal
+conductivity~($\kappa$). \vspace{2mm}
+\myitem Estimates are {\color{pigment}uncertain} and severely
+{\color{pigment}under-predicted}.
+\begin{itemize}
+  \item Simulation length-scales $\ll$ phonon mean free path. \vspace{1mm}
+  \item Thermostats reduce correlation b/w vibration modes.
+\end{itemize}
+
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{bg}
+
+\begin{frame}{Sources of Uncertainty}
+
+\begin{columns}
+\begin{column}{0.52\textwidth}
+
+\begin{itemize}
+\myitem Bulk thermal conductivity is size-dependent.
+\vspace{2mm}
+\myitem Variability in applied thermal gradient~(Kapitza~effect).
+\vspace{2mm}
+\myitem Choice of the inter-atomic potential.
+\vspace{2mm}
+\myitem Nominal estimates of the potential parameters.
+
+\end{itemize}
+\end{column}
+
+\begin{column}{0.48\textwidth}
+
+\begin{center}
+\begin{figure}[htbp]
+\vspace{-3mm}
+  \includegraphics[width=0.9\textwidth]{./Figures/cond_size}
+  \\ \vspace{2mm}
+  \includegraphics[width=0.9\textwidth]{./Figures/temp_plot}
+\end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{bg}
+
+\begin{frame}{Specific Research Goals}
+
+\begin{itemize}
+
+\myitem Quantify discrepancy in $\kappa$ between predictions and data.
+\begin{itemize}
+\item Construct a response surface for $\kappa(s,\frac{d\theta}{dx})$.
+\end{itemize}
+\vspace{2mm}
+\myitem Perform sensitivity analysis of the potential parameters.
+\begin{itemize}
+\item Estimate derivative-based sensitivity measures~(DGSM).
+\end{itemize}
+\vspace{2mm}
+\myitem Construct a reduced order surrogate for $\kappa$ using sparse
+NEMD predictions.
+\begin{itemize}
+\item Use the surrogate for forward propagation of uncertainty, and global
+sensitivity analysis. 
+\end{itemize}
+\vspace{2mm}
+\myitem Calibrate the \textit{important} parameters in a Bayesian setting.
+
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{\scshape Set-up}
+\subsection{setup}
+
+\begin{frame}{Problem Set-up}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+
+\begin{center}
+\begin{tikzpicture}
+\node[fill=white,inner sep=0pt] 
+{\rowcolors{1}{DeepSkyBlue!20}{DeepSkyBlue!5}
+	\resizebox{\columnwidth}{!}{
+  \begin{tabular}{l|c}
+%\hline
+	Lattice Constant, $a$ ($\angstrom$) & 5.43 \\ 
+	Width, Height ($\angstrom$) & 22$a$ \\ 
+	$\Delta t$  (ps) & 0.0005 \\
+	Boundary Condition & Periodic \\ 
+	Lattice Structure & Diamond \\ 
+	Inter-atomic Potential & Stillinger-Weber
+
+%\hline
+  \end{tabular}%
+	}
+};
+\end{tikzpicture}
+\end{center}
+
+\end{column}
+
+\begin{column}{0.5\textwidth}
+
+%\vspace{-5mm}
+\begin{center}
+\begin{figure}[htbp]
+        \includegraphics[width=0.9\textwidth]{./Figures/schematic}
+\end{figure}
+\vspace{3mm}
+%        \animategraphics[autopause,poster=first,loop,height=0.60\textwidth]{5}
+%        {./animation/snap}{0}{64}
+\end{center}
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{setup}
+\begin{frame}{Problem Set-up}
+
+%\vspace{-4mm}
+
+\begin{itemize}
+\myitem \textsc{Stages}:\\
+
+\begin{center}
+{\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{cyan}NVE} \hspace{5mm}
+$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
+\\ \vspace{1mm}
+\tiny \hspace{-5mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+ [Generate Data]
+\\ \vspace{1mm}
+
+\tiny{N: Number of Atoms~~~V: Volume~~~T: Temperature~~~E: Energy}
+\end{center}
+
+\normalsize
+
+\myitem \textsc{Observable}: Avg. energy exchange b/w thermostats~($q$)
+\vspace{2mm}
+
+\myitem \textsc{QoI}: Bulk thermal conductivity ($\kappa$)
+
+\begin{empheq}[box=\tcbhighmath]{align}
+  \kappa = \frac{q}{\left|\frac{dT}{dx}\right|} \nonumber
+\end{empheq}
+
+\vspace{2mm}
+
+\myitem Appropriate selection of {\color{pigment}width}, 
+{\color{pigment}height}, and {\color{pigment}simulation-time} was ensured.  
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{\scshape Discrepancy}
+\subsection{response}
+\begin{frame}{Response Surface: Discrepancy}
+
+\begin{columns}
+\begin{column}{0.52\textwidth}
+
+\begin{itemize}
+\myitem PC representation of the discrepancy, 
+$\epsilon_{\mbox{\tiny{d}}}$:
+
+\begin{empheq}[box=\tcbhighmath]{align}
+\epsilon_{\mbox{\tiny{d}}} \approx \mathcal{\epsilon}_{\mbox{\tiny{d}}}^{\mbox{\tiny{PCE}}} = 
+\sum_{\bm{k}\in\mathcal{I}} c_{\bm{k}}(T)\Psi_{\bm{k}}(\bm{\xi(\theta)})
+\nonumber
+\end{empheq}
+
+\end{itemize}
+\end{column}
+
+\begin{column}{0.48\textwidth}
+
+\begin{center}
+\begin{figure}[htbp]
+\vspace{-3mm}
+  \includegraphics[width=0.95\textwidth]{./Figures/realz_quad300K}
+  \\ \vspace{1mm}
+  \includegraphics[width=0.9\textwidth]{./Figures/PCspectrum_300}
+\end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
 \end{document}

### 2018-04-11 Slides/r1/md_si.tex
..

@@
 \usepackage{tikz}
+\usetikzlibrary{mindmap}
+\usetikzlibrary{arrows.meta}
 \usetikzlibrary{decorations.fractals}
@@
 \definecolor{pigment}{rgb}{0.2, 0.2, 0.6}
+\DeclareMathOperator*{\argmin}{arg\,min}
 %\usepackage{flexisym}
@@
 
-% Custom block environment
-% Custom block environment
-\newenvironment<>{varblock}[2][.9\textwidth]{%
-  \setlength{\textwidth}{#1}
-  \begin{actionenv}#3%
-    \def\insertblocktitle{#2}%
-    \par%
-    \usebeamertemplate{block begin}}
-  {\par%
-    \usebeamertemplate{block end}%
-  \end{actionenv}}
+\setbeamertemplate{blocks}[rounded][shadow=false]
+\addtobeamertemplate{block begin}{\pgfsetfillopacity{0.8}}{\pgfsetfillopacity{1}}
+\setbeamercolor{structure}{fg=mygreen}
+\setbeamercolor*{block title example}{fg=blue!50,
+bg= blue!10}
+\setbeamercolor*{block body example}{fg= blue,
+bg= blue!5}
 
@@
 
+\vspace{7mm}
+\begin{center}
+\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept color=orange!40, 
+    level 1/.append style={level distance=5cm,sibling angle=90},
+    level 2/.append style={level distance=3cm,sibling angle=45},transform canvas={scale=0.5}]
+
+    \node{Non-Equlibrium Molecular Dynamics}
+   child [concept color=blue!30]{ node {Noise}
+        child { node {Experiment Data}}
+        child { node {MD Simulation}}
+    }
+    child [concept color=yellow!30]{ node {Model Inadequacy}
+    child { node {Upscaling}}
+        child { node {Missing Physics}}
+    }
+    child [concept color=green!30]{ node {Inter-atomic Potential}
+        child { node {Potential Selection}}
+        child { node {Parameter Values}}
+         }
+    child [concept color=red!30]{ node {Simulation Set-up}
+        child { node {System Size}}
+        child { node {Heat flux/Thermal gradient}}
+        child { node {Duration}}
+    };
+
+  \end{tikzpicture}
+  \end{center}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{bg}
+
+\begin{frame}{Sources of Uncertainty}
+
 \begin{columns}
@@
 \vspace{3mm}
-%        \animategraphics[autopause,poster=first,loop,height=0.60\textwidth]{5}
-%        {./animation/snap}{0}{64}
+        \animategraphics[autoplay,poster=first,loop,height=0.60\textwidth]{5}
+        {./animation/snap}{0}{64}
 \end{center}
@@
 
-\begin{empheq}[box=\tcbhighmath]{align}
-  \kappa = \frac{q}{\left|\frac{dT}{dx}\right|} \nonumber
-\end{empheq}
+\begin{center}
+\begin{tcolorbox}[width=0.3\textwidth,height=0.2\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\kappa = \frac{q}{\left|\frac{dT}{dz}\right|} \nonumber
+\ee
+\end{tcolorbox}
+\end{center}
+
+%\begin{empheq}[box=\tcbhighmath]{align}
+%  \kappa = \frac{q}{\left|\frac{dT}{dz}\right|} \nonumber
+%\end{empheq}
 
@@
 
-\section{\scshape Discrepancy}
+\section{\scshape Response Surface}
 \subsection{response}
@@
 $\epsilon_{\mbox{\tiny{d}}}$:
+\vspace{-2mm}
 
-\begin{empheq}[box=\tcbhighmath]{align}
+\begin{center}
+\begin{tcolorbox}[width=0.9\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\scriptsize
+\be
 \epsilon_{\mbox{\tiny{d}}} \approx \mathcal{\epsilon}_{\mbox{\tiny{d}}}^{\mbox{\tiny{PCE}}} = 
@@
  \nonumber
-\end{empheq}
+\ee
+\end{tcolorbox}
+\end{center}
+
+\vspace{2mm}
+\normalsize
+
+\myitem Uncertain parameters, $\bm{\theta}$:~$\{L,\frac{dT}{dz}\}$
+\scriptsize
+\begin{center}
+$L~\sim~\mathcal{U}[50a, 100a](\angstrom)$ \\ \vspace{2mm}
+$\frac{dT}{dz}~\sim~\mathcal{U}[\frac{1.5}{a}, \frac{2.5}{a}](\frac{K}{\angstrom})$
+
+\end{center}
 
@@
 
+%___________________________NEW SLIDE______________________________________
+
+\subsection{response}
+\begin{frame}{Verification}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\vspace{-1mm}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.8\textwidth]{./Figures/err2D_s}
+  \end{figure}
+\end{center}
+%\vspace{-2mm}
+\scriptsize
+
+\begin{center}
+\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-3mm}
+\scriptsize
+\be
+ \varepsilon_{\tiny{\mbox{L-2}}} = \frac{\left[\sum_{j}(\epsilon_{\tiny{\mbox{d},j}}^{\mbox{\tiny{MD}}} - 
+ \epsilon_{\tiny{\mbox{d},j}}^{\mbox{\tiny{PCE}}})^2\right]^{\frac{1}{2}}}{\left[\sum_j(\epsilon_{\tiny{\mbox{d},j}}
+ ^{\mbox{\tiny{MD}}})^2\right]^{\frac{1}{2}}} \sim \mathcal{O}(10^{-3}) \nonumber
+ \ee
+\end{tcolorbox}
+\end{center}
+
+\end{column}
+
+\begin{column}{0.5\textwidth}
+
+\begin{center}
+\begin{figure}[htbp]
+\vspace{-3mm}
+  \includegraphics[width=0.8\textwidth]{./Figures/err2D_300}
+  \\ \tiny{300~K} \vspace{1mm} \\
+  \includegraphics[width=0.8\textwidth]{./Figures/err2D_500}
+  \\ \tiny{500~K}
+\end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{response}
+\begin{frame}{Direct Method}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.85\textwidth]{./Figures/kinv_300}
+  \\ \vspace{1mm} \tiny{300~K}
+  \end{figure}
+\end{center}
+\end{column}
+\hspace{-6mm}
+\begin{column}{0.5\textwidth}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.85\textwidth]{./Figures/kinv_500}
+   \\ \vspace{1mm}\tiny{500~K}
+  \end{figure}
+\end{center}
+\end{column}
+
+\end{columns}
+
+\vspace{2mm}
+\begin{itemize}
+\myitem y-intercept of the straight line fit  to the above plot provides an estimate of the bulk thermal conductivity. 
+\end{itemize}
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{\scshape Potential}
+\subsection{sw}
+
+\begin{frame}{The Stillinger-Weber Potential}
+
+\scriptsize
+\vspace{10mm}
+\tikz[overlay, remember picture] \node at (2.9,1) {
+\begin{tcolorbox}[width=0.34\textwidth,colback=DeepSkyBlue4,notitle,colframe=DeepSkyBlue4,colupper=white]
+\textsc{Functional Form}
+\end{tcolorbox}
+};
+\tikz[overlay, remember picture] \node at (5.3,-0.16) {
+\begin{tcolorbox}[width=0.8\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\Phi(1,\ldots,N) = \sum\limits_{i,j(i<j)}v_{ij}^{(2)}(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}v_{ij}^{(3)}(\lambda,\gamma)\nonumber
+\ee
+\end{tcolorbox}
+};
+\normalsize
+
+\vspace{15mm}
+\textsc{Shortcomings}
+
+\begin{itemize}
+\myitem {\color{pigment}Inadequate} functional representation. 
+\vspace{1mm}
+\myitem Estimates based on a {\color{pigment}limited} search. 
+\vspace{1mm}
+\myitem Do not account for {\color{pigment}measurement error} and {\color{pigment}MD noise}. 
+\vspace{1mm}
+\myitem {\color{pigment}Parametric uncertainties} were not considered. 
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sw}
+
+\begin{frame}{The Stillinger-Weber Potential}
+
+\scriptsize
+\vspace{10mm}
+\tikz[overlay, remember picture] \node at (2.9,1) {
+\begin{tcolorbox}[width=0.34\textwidth,colback=DeepSkyBlue4,notitle,colframe=DeepSkyBlue4,colupper=white]
+\textsc{Functional Form}
+\end{tcolorbox}
+};
+\tikz[overlay, remember picture] \node at (5.3,-0.16) {
+\begin{tcolorbox}[width=0.8\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\Phi(1,\ldots,N) = \sum\limits_{i,j(i<j)}v_{ij}^{(2)}(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}v_{ij}^{(3)}(\lambda,\gamma)\nonumber
+\ee
+\end{tcolorbox}
+};
+\normalsize
+
+\vspace{15mm}
+\textsc{Mitigation Strategies}
+
+\begin{itemize}
+\myitem {\color{pigment}Sensitivity Analysis} of the parameters. 
+\vspace{1mm}
+\myitem {\color{pigment}Forward propagation} of the uncertainty. 
+\vspace{1mm}
+\myitem {\color{pigment}Bayesian calibration} of the key parameters.
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{Sensitivity}
+\subsection{sense}
+
+\begin{frame}{Sensitivity Analysis}
+
+\begin{columns}
+\begin{column}{0.55\textwidth}
+\textsc{Challenges}
+
+\vspace{2mm}
+\begin{itemize}
+
+\Myitem Global sensitivity analysis is {\color{pigment}computationally intractable}.
+\vspace{2mm}
+\Myitem Perturbing potential parameters $\rightarrow$ loss of {\color{pigment}structural integrity}. 
+\end{itemize}
+\end{column}
+
+\begin{column}{0.45\textwidth}
+\begin{center}
+%\begin{figure}[htbp]
+ % \includegraphics[width=0.85\textwidth]{./Figures/unstable}
+ % \end{figure}
+  \animategraphics[autopause,poster=first,loop,height=0.90\textwidth]{5}
+       {./anim_unstable/snap}{0}{49}
+
+  \end{center}
+
+ \end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sense}
+
+\begin{frame}{Sensitivity Analysis}
+\begin{itemize}
+\myitem Derivative-based sensitivity measures (DGSM) are estimated to identify \textit{unimportant} parameters.
+
+\hspace{-5mm}
+\tikz[overlay, remember picture] \node at (2,-1) {
+\scriptsize
+\begin{tcolorbox}[width=0.27\textwidth,colback=red!20,notitle,colframe=red!20,colupper=DeepSkyBlue4]
+\vspace{-3mm}
+\be
+\hspace{-4.2mm}
+\mu_i = \mathbb{E}\left[\left(\frac{\partial G(\bm{\theta})}{\partial \theta_i}\right)^{2}\right] \hspace{4mm} \rightarrow \nonumber
+\ee
+\end{tcolorbox}
+};
+
+\hspace{-5mm}
+\tikz[overlay, remember picture] \node at (5.56,-0.5) {
+\scriptsize
+\begin{tcolorbox}[width=0.20\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-3mm}
+\be
+\hspace{-4.5mm}
+\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}  \hspace{2mm}\rightarrow \nonumber
+\ee
+\end{tcolorbox}
+};
+
+\hspace{-5mm}
+\tikz[overlay, remember picture] \node at (8.6,0) {
+\scriptsize
+\begin{tcolorbox}[width=0.25\textwidth,colback=green!20,notitle,colframe=green!20,colupper=DeepSkyBlue4]
+\vspace{-3mm}
+\be
+\hspace{-3mm}
+\mathcal{T}_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})   \nonumber
+\ee
+\end{tcolorbox}
+};
+
+\vspace{12mm}
+
+\myitem DGSM estimates are used to compute upper bound on Sobol total effect index~($\mathcal{T}_i$).
+
+\end{itemize}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sense}
+
+\begin{frame}{Sensitivity Analysis}
+\vspace{2mm}
+
+\begin{itemize}
+
+\myitem Add an NPT ensemble prior to NVT and run it for a sufficiently long time. 
+\vspace{2mm}
+
+\begin{center}
+{\color{gray}NPT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} 
+{\color{cyan}NVE} \hspace{5mm}
+$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
+\\ \vspace{1mm}
+\tiny [Relax system length] \hspace{1mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+ [Generate Data]
+\\ \vspace{1mm}
+
+\tiny{N: Number of Atoms~~~P: Pressure~~~V: Volume~~~T: Temperature~~~E: Energy}
+\end{center}
+
+\end{itemize}
+
+\begin{center}
+\vspace{-2mm}
+\begin{figure}[htbp]
+  \includegraphics[width=0.6\textwidth]{./Figures/lx_npt}
+  \end{figure}
+\end{center}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sense}
+
+\begin{frame}{Parameter Screening}
+
+\begin{algorithm}[H]
+\SetAlgoLined
+\scriptsize
+\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$.}\;
+\nonl\scriptsize\texttt{\color{blue}$\%~d$: Number of parameters}\;
+\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.}\;
+\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$}\;
+\texttt{Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values for $\theta_i$}\;
+\texttt{Set $k$ = 1}\;
+%\nonl\scriptsize\texttt{\color{blue}$\%~k$: Iteration counter}\;
+\Repeat{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
+               $max\_pdev$~$>~\tau$)}{
+\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$.}\;
+\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.}\;
+\texttt{Compute and store model evaluations at the $n_k(d+1)$ points.}\;
+\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.}\;
+\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values.}\;
+\texttt{Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.}\;
+\nonl\scriptsize\texttt{\color{blue}$\%~max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
+\texttt{Set $k$ = $k$ + 1}\;
+}
+\end{algorithm}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sense}
+
+\begin{frame}{Parameter Screening}
+
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.7\textwidth]{./Figures/ub}
+  \end{figure}
+\end{center}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{\scshape Surrogate}
+\subsection{sur}
+
+\begin{frame}{Reduced Order Surrogate}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+
+\begin{itemize}
+
+\myitem PCE for $\kappa$:
+
+\scriptsize
+\begin{center}
+\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\kappa  = \sum\limits_{\bm{s}\in\mathcal{A}} c_{\bm{s}}(T)\Psi_{\bm{s}}(\bm{\xi})\nonumber
+\ee
+\end{tcolorbox}
+\vspace{1mm} 
+\tiny {$\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$}
+\end{center}
+
+\normalsize
+\vspace{2mm}
+\myitem Regularized least-squares minimization problem:
+
+\scriptsize
+\begin{center}
+\begin{tcolorbox}[width=1.2\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\hspace{-3mm}
+\hat{\bm{c}} = \argmin\limits_{\bm{c}\in \mathbb{R}^{|\mathcal{A}|}}\mathbb{E}\left[\left(\bm{c}^{\tiny{\mbox{T}}}\Psi(\bm{\xi(\theta)}) - 
+\kappa_{\bm{\theta}}^{\tiny{\mbox{MD}}}\right)^2\right]~+~\lambda\|\bm{c}\|_1 \nonumber
+\ee
+\end{tcolorbox}
+\end{center}
+
+\end{itemize}
+
+\end{column}
+
+\begin{column}{0.5\textwidth}
+\vspace{-11mm}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=1.0\textwidth]{./Figures/PCE5D_eloo}
+  \end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sur}
+
+\begin{frame}{Verification}
+
+\begin{columns}
+\begin{column}{0.6\textwidth}
+\textsc{L-2 Norm}
+\vspace{5mm}
+\begin{center}
+\scriptsize
+\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\hspace{-5mm}
+\epsilon_{\mbox{\tiny{L-2}}} = 
+\frac{\left[\sum\limits_{i=1}^{N=25}\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)}) - 
+\mathcal{M}^{PCE}(\bm{\theta}_{\mbox{\tiny{5D}}}^{(i)})\right)^{2}\right]^{\frac{1}{2}}}{\left[\sum_{i=1}^{N}
+\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)})\right)^2\right]^{\frac{1}{2}}} \rightarrow \mathcal{O}(10^{-2})
+\nonumber
+\ee
+\end{tcolorbox}
+\end{center}
+
+\end{column}
+
+\hspace{3mm}
+\begin{column}{0.4\textwidth}
+\hspace{5mm}\textsc{Probabilistic}
+
+\begin{center}
+\begin{figure}[htbp]
+\hspace{12mm}
+  \includegraphics[width=0.95\textwidth]{./Figures/PCE5D_kde}
+  \end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\subsection{sur}
+
+\begin{frame}{Global Sensitivity Analysis}
+
+\begin{columns}
+\begin{column}{0.5\textwidth}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.9\textwidth]{./Figures/PCE5D_gsa}
+  \\ \scriptsize{10$^{6}$ samples}
+  \end{figure}
+\end{center}
+\end{column}
+\hspace{-9mm}
+\begin{column}{0.5\textwidth}
+\begin{center}
+\begin{figure}[htbp]
+  \includegraphics[width=0.9\textwidth]{./Figures/ub}
+    \\ \scriptsize{25 samples}
+  \end{figure}
+\end{center}
+\end{column}
+
+\end{columns}
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+\section{\scshape Bayes}
+\subsection{bayes}
+
+\begin{frame}{Bayesian Calibration}
+
+\begin{columns}
+\begin{column}{0.55\textwidth}
+\begin{itemize}
+\myitem Bayes' rule:
+
+\begin{center}
+\scriptsize
+\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-2mm}
+\be
+\mathcal{P}(\bm{X}\vert \bm{Y}) \propto \mathcal{P}(\bm{Y}\vert\bm{X})\mathcal{P}(\bm{X})
+\nonumber
+\ee
+\end{tcolorbox}
+\vspace{1mm}
+\tiny{$\bm{X}:\{\alpha,\gamma\}$}
+\end{center}
+
+\vspace{2mm}
+
+\myitem Likelihood, $\mathcal{P}(\bm{Y}\vert\bm{X})$:
+\begin{center}
+\scriptsize
+\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
+\vspace{-3mm}
+\be
+\mathcal{P}(\bm{Y}\vert\bm{X}) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left[-\frac{(\kappa_{\tiny{\mbox{E}}} - 
+\kappa_{\tiny{\mbox{MD}}})^2}{2\sigma^2}\right]
+\nonumber
+\ee
+\end{tcolorbox}
+\end{center}
+
+\end{itemize}
+\end{column}
+
+\hspace{3mm}
+\begin{column}{0.45\textwidth}
+
+\begin{center}
+\vspace{-20mm}
+\begin{figure}[htbp]
+\hspace{3mm}
+  \includegraphics[width=1.0\textwidth]{./Figures/gl}
+  \end{figure}
+\end{center}
+
+\end{column}
+\end{columns}
+
+\end{frame}
+
+%___________________________NEW SLIDE______________________________________
+
+%\subsection{conc}
+
+\begin{frame}{Concluding Remarks}
+
+\end{frame}
+
 \end{document}

### 2018-04-12 Slides/r1/md_si.tex
..

@@
 {\color{pigment}non-metallic} systems (C,Si,Ge).
+\pause
 \vspace{2mm}
 \myitem System subjected to a temperature gradient using thermostats.
+\pause
 \vspace{2mm}
@@
 the thermostats is used in Fourier's law to estimate bulk thermal
-conductivity~($\kappa$). \vspace{2mm}
+conductivity~($\kappa$). 
+\pause
+\vspace{2mm}
 \myitem Estimates are {\color{pigment}uncertain} and severely
@@
 
-    \node{Non-Equlibrium Molecular Dynamics}
+    \node{Non-Equilibrium Molecular Dynamics}
    child [concept color=blue!30]{ node {Noise}
@@
 \begin{columns}
-\begin{column}{0.52\textwidth}
-
-\begin{itemize}
-\myitem Bulk thermal conductivity is size-dependent.
-\vspace{2mm}
-\myitem Variability in applied thermal gradient~(Kapitza~effect).
-\vspace{2mm}
-\myitem Choice of the inter-atomic potential.
-\vspace{2mm}
-\myitem Nominal estimates of the potential parameters.
-
-\end{itemize}
-\end{column}
-
-\begin{column}{0.48\textwidth}
-
-\begin{center}
-\begin{figure}[htbp]
-\vspace{-3mm}
+\begin{column}{0.5\textwidth}
+
+\begin{center}
+\begin{figure}[htbp]
   \includegraphics[width=0.9\textwidth]{./Figures/cond_size}
-  \\ \vspace{2mm}
+\end{figure}
+\end{center}
+
+\end{column}
+\hspace{-15mm}
+\begin{column}{0.5\textwidth}
+
+\begin{center}
+\begin{figure}[htbp]
   \includegraphics[width=0.9\textwidth]{./Figures/temp_plot}
@@
 \begin{itemize}
-\item Construct a response surface for $\kappa(s,\frac{d\theta}{dx})$.
-\end{itemize}
+\item Construct a response surface for $\kappa(s,\frac{d\theta}{dz})$.
+\end{itemize}
+\pause
 \vspace{2mm}
@@
 \begin{itemize}
-\item Estimate derivative-based sensitivity measures~(DGSM).
-\end{itemize}
+\item Estimate derivative-based global sensitivity measures~(DGSM).
+\end{itemize}
+\pause
 \vspace{2mm}
@@
 \end{itemize}
+\pause
 \vspace{2mm}
@@
 };
+\pause
 \normalsize
@@
 \\ \vspace{1mm}
-\tiny [Relax system length] \hspace{1mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
+\tiny [Relax system length] \hspace{1mm}[Equilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
  [Generate Data]
@@
 \begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
-\vspace{-2mm}
+\vspace{-3mm}
 \be
@@
 \begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
-\vspace{-3mm}
+\vspace{-4mm}
 \be
@@
 
+\begin{itemize}
+
+\myitem Discrepancy between NEMD predictions and experiments is captured using a response surface. 
+\pause
+\vspace{2mm}
+\myitem The impact of variability in applied thermal gradient seems negligible at least in the considered interval. 
+\pause
+\vspace{2mm}
+\myitem Sensitivity analysis using DGSM could help mitigate computational costs.  
+\pause
+\vspace{2mm}
+\myitem NEMD predictions are largely sensitivity towards $\alpha$ and $\gamma$.
+\pause
+\vspace{2mm}
+\myitem Calibration should be performed in a Bayesian setting to account for all possible errors and uncertainties.  
+\pause
+\vspace{2mm}
+\myitem Strategies presented can be easily extended to other systems and potentials.
+
+\end{itemize}
+
 \end{frame}

### 2018-04-29 Paper/ack.tex
..

@@
 M. Vohra and S. Mahadevan gratefully acknowledge funding support from the
-National Science Foundation Award $\#$. Molecular
+National Science Foundation (Grant No. 1404823, CDSE Program). Molecular
 dynamics simulations were performed using resources at the advanced computing
@@
 M. Vohra is grateful to the ACCRE staff for their technical guidance
-and support. He would also like to sincerely thank Dr. Alen Alexanderian for
+and support. He would also like to sincerely thank Dr. Alen Alexanderian at NC State 
+University for
 insightful discussions pertaining to the derivative-based sensitivity analysis
-aspect of this work.
+in this work.

### 2018-04-29 Paper/bayes.tex
..

@@
 the so-called joint posterior probability distribution (referred to as the `posterior') of the uncertain model 
-parameters to be calibrated, using the Bayes' rule:
+parameters to be calibrated, using Bayes' rule:
 
@@
 predictions, whereas, the prior is an initial guess for the distribution of uncertain model parameters in an
-interval. It also accounts for the availability of an expert opinion pertaining to their estimates. 
+interval. It also accounts for the availability of the expert opinion pertaining to their estimates. 
 The posterior provides an estimate of the most likely value of the uncertain model parameters based on
@@
 Additionally, the posterior is often used to quantify the uncertainty associated with model predictions.
-Several algorithms based on Markov chain Monte Carlo (MCMC) technique are available for
+Several algorithms based on the Markov chain Monte Carlo (MCMC) technique are available for
 sampling the posterior~\cite{Haario:2001, Haario:2006,Xu:2014}.
@@
 Evaluating the joint posterior of $\alpha$ and $\gamma$ using MCMC typically requires a large amount of
-computational effort and is not the focus on this work. Instead, we compute and plot the joint likelihood on
+computational effort and is not the focus of this work. Instead, we compute and plot the joint likelihood on
 a 2D cartesian grid described by $\alpha$ and $\gamma$ using Eq.~\ref{eq:like} as illustrated in
-Figure~\ref{fig:like}(a). For this purpose, we consider $\alpha$ and $\gamma$ to be
+Figure~\ref{fig:like}(a). For this purpose, we consider the priors of $\alpha$ and $\gamma$ to be
 independent and uniformly distributed in the intervals, [1.62,1.98] and [1.08,1.32] respectively. 
@@
 and experimental data~($\kappa_{\tiny{\mbox{E}}}$). Experimental data for $\kappa_{\tiny{\mbox{E}}}$ at 300~K
-(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood.
+(149~W/m/K~\cite{Shanks:1963}) is used to compute the joint likelihood. It must be noted that the likelihood
+function in Eq.~\ref{eq:like} could be refined further by accounting for a model discrepancy term and hence
+calibrating the associated parameters in addition to the uncertain model inputs~\cite{Kennedy:2001,Ling:2014}.
 
@@
   \end{tabular}
-\caption{(a) A joint likelihood as estimated using Eq.~\ref{eq:like} is plotted on a 2D cartesian grid
- ($\alpha\times\gamma$). Point corresponding to the maximum likelihood (MLE) is also highlighted.
- The likelihood is plotted along a line passing through MLE and parallel to the $\alpha$-axis
- in (b), and $\gamma$-axis in (c).}
+\caption{(a) The joint likelihood of ($\alpha$,$\gamma$) as estimated using Eq.~\ref{eq:like} is plotted
+on a 2D cartesian grid. The maximum likelihood estimate (MLE) is also highlighted.
+Marginal likelihoods for $\alpha$ and $\gamma$ are plotted in (b) and (c) respectively.}
 \label{fig:like}
@@
 
-Approximate marginal distributions for
+Marginal distributions for
 $\alpha$ and $\gamma$ are shown in Figure~\ref{fig:like}(b) and Figure~\ref{fig:like}(c) respectively. 
-It must be noted that the joint likelihood plot is essentially for the purpose of illustration. The actual posterior
-should be evaluated using a substantially large set of experimental data for bulk thermal conductivity as a function
-of temperature, and surrogates for NEMD predictions
-need to be constructed (as discussed in Section~\ref{sec:ros}) at each temperature for which the data is made
-available in order to reduce computational effort. 
-The dimensionality of the surrogate could potentially be reduced a priori using DGSM and a posteriori using
-Sobol sensitivity analysis as presented in this work.
+As mentioned above, the joint likelihood plot is based on the bulk thermal conductivity measurement at 300~K.
+An enhanced set of experimental measurements at different bulk temperatures would help improve the
+accuracy of the calibration process considering the measurement noise is not too large. Moreover, it would
+help capture the correlation between calibration parameters across temperatures at which the data is
+available. However, a reduced-order surrogate would be needed at each temperature in order to make the
+MCMC tractable.

### 2018-04-29 Paper/cover.tex
intro pass 1 complete
..

@@
 \textsc{
-Facilitating Uncertainty Analysis in Non-Equilibrium Molecular Dynamics Simulations for
+Uncertainty Quantification in Non-Equilibrium Molecular Dynamics Simulations of
 Thermal Transport
@@
 
-Manav Vohra$^{1}$, Ali Y. Nobakht$^{2}$, Seungha Shin$^{2}$, Sankaran Mahadevan$^{1}$
+Manav Vohra$^{1}$, Ali Yousefzadi Nobakht$^{2}$, Seungha Shin$^{2}$, Sankaran Mahadevan$^{1}$
 

### 2018-04-29 Paper/intro.tex
..

@@
 
-Classical Molecular Dynamics (MD) is commonly used to study thermal transport by means of
-interactions between phonons in material systems comprising non-metallic elements such
+Classical molecular dynamics (MD) is commonly used to study thermal transport by means of
+phonons in material systems comprising non-metallic elements such
 as carbon, silicon, and germanium~\cite{Dumitrica:2010}. 
 A major objective for many such studies is the
-estimation of bulk thermal conductivity of the system. One of the most commonly used approach,
+estimation of bulk thermal conductivity of the system. One of the most commonly used approaches,
 regarded as the direct method~\cite{Schelling:2002,Turney:2009,Zhou:2009,Landry:2009,
@@
 of a heat flux or a temperature gradient by means of thermostatting, across the system. 
-Corresponding steady-state temperature gradient in the former or the heat exchange between
+The corresponding steady-state temperature gradient in the former or the heat exchange between
 the two thermostats in the latter, is used to estimate the bulk thermal conductivity (at a given
 length or size) using 
-Fourier's law. Computations are performed for a range of system lengths and the inverse
-of thermal conductivity is plotted against the inverse of length. The y-intercept of a
+Fourier's law. However, when the simulation domain is comparable to or smaller than the
+mean free path, thermal conductivity estimates from the direct method depends on the
+distance between the two thermostats, due to significant contribution of boundary scattering.
+Hence, to estimate the bulk thermal conductivity, computations are performed for a range of
+system lengths and the inverse
+of thermal conductivity is plotted against the inverse of length. The $y$-intercept of a
 straight line fit to the observed trend is considered as the bulk thermal conductivity 
@@
 Although widely used, the direct method is known to severely under-predict
-the bulk thermal conductivity as compared to experimental 
+the bulk thermal conductivity compared to experimental 
 measurements~\cite{Haynes:2014,Shanks:1963}. This is primarily
-due to length scales used in simulation that are several orders of magnitude smaller
+due to length scales used in the simulation that are several orders of magnitude smaller
 than those used in an experiment. As a result, the sample length is much smaller than the
-bulk phonon mean free path leading to a so-called ballistic transport of the phonons.
+bulk phonon mean free path leading to the so-called ballistic transport of the phonons.
 The mean free path of such phonon modes is limited to the system size that reduces their
@@
 introduction of thermostats typically reduces the correlation between vibrations of 
-different atoms (regarded as Kapitza effect~\cite{Stevens:2007}) potentially reducing
-the thermal conductivity
+different atoms potentially reducing the thermal conductivity
 further~\cite{Evans:2008}. Estimation of thermal conductivity using the
 direct method is therefore impacted by the choice of system size and potentially due to
-variability in the thermal gradient experienced by the system due to thermostatting.
+fluctuations in the thermal gradient experienced by the system due to thermostatting.
 
@@
 of a given potential. For instance, in the case of crystalline Si, the Stillinger-Weber (SW)
-is a widely used inter-atomic potential. However, as discussed by Stillinger and Weber
-in~\cite{Stillinger:1985}, the proposed nominal values of individual parameters are based
-on a limited search in the 7D parameter space while ensuring structural stability and
+inter-atomic potential is widely used. However, as discussed by Stillinger and Weber
+in~\cite{Stillinger:1985}, their proposed nominal values of individual parameters were based
+on a limited search in a 7D parameter space while ensuring structural stability and
 reasonable agreement with experiments. It is therefore likely that these nominal estimates
@@
 spatial temperature 
-distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implement an uncertainty
+distribution during heat conduction. Jacobson et al. in~\cite{Jacobson:2014} implemented an uncertainty
 quantification framework to optimize a coarse-grained model for predicting the properties of monoatomic
- water. While these are significant contributions, it is only until recently 
+ water. While these are significant contributions, it is only recently 
 that researchers have started accounting for the presence of uncertainties in MD predictions in a
@@
 
-In the present work, we focus our efforts on uncertainty analysis in predictions of NEMD simulations
+In the present work, we focus our efforts on uncertainty analysis in the predictions of NEMD simulations
 for phonon transport using a silicon bar. An overview of the set-up for the simulations is
@@
 exhibit large discrepancies with experimental observations depending upon system size and potentially
-due to variability in the applied thermal gradient. Additionally, the thermal conductivity estimates are
+due to fluctuations in the applied thermal gradient. Additionally, the thermal conductivity estimates are
 tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
@@
 Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 
-variability in predictions~(Section~\ref{sec:sense}).
+uncertainty in the predictions~(Section~\ref{sec:sense}).
 Third, we exploit our findings from sensitivity analysis to 
 construct a reduced order surrogate for uncertainty analysis~(Section~\ref{sec:ros}). 
-Fourth, we illustrate calibration
-of the important parameters in a Bayesian setting to evaluate their posterior
+Fourth, we illustrate the calibration
+of important parameters in a Bayesian setting to evaluate their posterior
 distributions~(Section~\ref{sec:bayes}). Construction of the
@@
 case of NEMD. We therefore employ polynomial chaos (PC) surrogates~\cite{Xiu:2002,Ghanem:1990}
-using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce computational effort pertaining
+using non-intrusive spectral approaches~\cite{Olivier:2010} to reduce the computational effort pertaining
 to the aforementioned objectives. Moreover, since the construction of a PC surrogate itself can be
-expensive, we demonstrate in Section~\ref{sec:sense}, a novel approach that implements derivative-based
-sensitivity measures~\cite{Sobol:2010} to a priori reduce the dimensionality of the surrogate while
+expensive, we demonstrate a novel approach in Section~\ref{sec:sense} that implements derivative-based
+sensitivity measures~\cite{Sobol:2010} to reduce the dimensionality of the surrogate a priori while
 ensuring reasonable predictive accuracy.

### 2018-04-29 Paper/ros.tex
..

@@
-\section{Reduced Order Surrogate}
+\section{Reduced-order Surrogate}
 \label{sec:ros}
@@
 In this section, we focus our attention on constructing a surrogate that captures the dependence of
-uncertainty in NEMD predictions for the bulk thermal conductivity ($\kappa$) on input variability
+uncertainty in NEMD predictions of the bulk thermal conductivity ($\kappa$) on input uncertainty
 in the SW potential parameters. The surrogate is a powerful tool that greatly minimizes
 the computational
-effort required for forward propagation of the uncertainty from input parameters to the observable,
-Sobol sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
+effort required for forward propagation of the uncertainty from input parameters to the output,
+Sobol\textquotesingle~sensitivity analysis, and Bayesian calibration of the uncertain model parameters. Once again,
 we use polynomial chaos (used to construct response surfaces for discrepancy in
@@
 algorithm~\cite{Blatman:2011}. Furthermore, since the NEMD simulations are compute-intensive,
-estimating the PC coefficients in the 7D parameter space would still require large amount of
+estimating the PC coefficients in the 7D parameter space would still require a large amount of
 computational resources. Hence, we explore the possibility of reducing the dimensionality of
@@
 exploit our observations in Figure~\ref{fig:ub} where a significant
-jump in $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
+jump in the $\hat{\mathcal{C}_i\mu_i}$ estimate is seen from $A$ to $B$ and thereby construct the 
 PC surrogate in a 5D parameter space by fixing $B$ and $p$ at their nominal values. In the above
@@
 below in Eq.~\ref{eq:loo}, against the number of model realizations used to construct the 5D
-PC surrogate. UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$ and constructing
-the surrogate.
+PC surrogate. The software, UQLab~\cite{Marelli:2014} was used for estimating $\epsilon_{\tiny{\mbox{LOO}}}$
+and constructing the surrogate. The leave-one-out cross validation error ($\epsilon_{\tiny{\mbox{LOO}}}$) is
+computed as:
 
@@
  \begin{center}
-  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_eloo}
+  \includegraphics[width=0.65\textwidth]{./Figures/PCE5D_eloo}
 \caption{A convergence study for the 5D PCE wherein the leave-one-out
@@
 using NEMD predictions (Model) at 25 points in the 7D parameter space and a probability distribution obtained 
-using kernel density estimation of  reduced order surrogate estimates of $\kappa$ for 10$^6$ samples in the 5D
+using kernel density estimation of  reduced-order surrogate estimates of $\kappa$ for 10$^6$ samples in the 5D
 parameter space.}
@@
 10$^6$ samples in the 5D parameter space described by the SW potential parameters:~$\{A,q,\alpha,\lambda,\gamma\}$.
-It is observed that the probability distribution (PDF) based on estimates from the reduced order surrogate compares
+It is observed that the probability density function (PDF) based on estimates from the reduced-order surrogate compares
 favorably with the histogram. Specifically, the corresponding mode values for $\kappa$ from the two plots are
@@
 the bulk thermal conductivity distribution as observed in the histogram. 
-Hence, the reduced order surrogate is verified for accuracy in both cases. 
+Hence, the reduced-order surrogate is verified for accuracy in both cases. 
 \bigskip
 
-As mentioned earlier, a PC surrogate can be used to estimate Sobol global sensitivity indices in a 
-straightforward manner~\cite{Sudret:2008}. Sobol first order and total effect sensitivity indices as estimated
-using the reduced order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
+As mentioned earlier, a PC surrogate can be used to estimate the Sobol\textquotesingle~global sensitivity indices in a 
+straightforward manner~\cite{Sudret:2008}. The Sobol\textquotesingle~first order and total effect sensitivity indices estimated
+using the reduced-order surrogate and $10^{6}$ samples in the 5D parameter space are plotted using bar-graphs in
 Figure~\ref{fig:gsa}.
@@
  \begin{center}
-  \includegraphics[width=0.70\textwidth]{./Figures/PCE5D_gsa}
-\caption{Sobol first-order and total effect sensitivity indices as obtained using the reduced order PC
-surrogate and 10$^{6}$ samples in the 5D parameter space. }
+  \includegraphics[width=0.65\textwidth]{./Figures/PCE5D_gsa}
+\caption{Sobol\textquotesingle~first-order and total effect sensitivity indices of the SW potential parameters
+w.r.t the bulk thermal
+conductivity as obtained using the reduced order PC surrogate and 10$^{6}$ samples in the 5D parameter space. }
 \label{fig:gsa}
@@
 parameter space. However, the DGSM estimate for $\gamma$ was found to be the highest in that case. 
-While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, Sobol
-indices for the three parameters are estimated to be smaller by an order of magnitude compared to those
+While sensitivity towards $A$, $q$, and $\lambda$ is observed to be comparatively less in both cases, the 
+Sobol\textquotesingle~indices for the three parameters are estimated to be smaller by an order of magnitude
+ compared to those
 for $\alpha$ and $\gamma$. Large quantitative disagreement in parametric sensitivity between DGSM and the 
-Sobol indices is however not unexpected essentially because the two metrics differ by construction.
+Sobol\textquotesingle~indices is however not unexpected essentially because the two metrics differ by construction.
 The former is based
@@
 agreement pertaining to parameter importance in the two approaches is quite encouraging. 
-Moreover, verification of the reduced order
-surrogate for accuracy increases our confidence in implementing DGSM to ascertain relative importance of the
+Moreover, verification of the reduced-order
+surrogate for accuracy increases our confidence in implementing DGSM to ascertain the relative importance of the
 SW potential parameters and hence perform uncertainty analysis for the present application with minimal

### 2018-04-29 Paper/sense.tex
..

@@
 However, according to Stillinger and Weber, the set of nominal
-values as provided below in Table~2 is based on a constrained search in the 7D parameter space
+values as provided below in Table~2 were based on a constrained search in the 7D parameter space
 to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.
@@
 
-It is noteworthy that the underlying analysis which lead to these estimates of the nominal values did not
+It is noteworthy that the underlying analysis which led to these estimates of the nominal values did not
 account for the presence of uncertainty due to
@@
 and parametric uncertainties. It is therefore likely that the proposed nominal estimates could be 
-improved depending upon the application. Hence, it is critical to understand the effects of variability in
+improved depending upon the application. Hence, it is critical to understand the effects of uncertainty in
 SW potential parameters on bulk thermal conductivity predictions using NEMD. For this purpose, a possible
 approach could involve a global sensitivity analysis of NEMD predictions on the SW potential parameters 
-by estimating the so-called Sobol indices~\cite{Sobol:2001}. However, obtaining converged estimates of
-Sobol indices typically requires tens of thousands of model evaluations. Since NEMD is compute-intensive,
-estimating the Sobol indices directly would be impractical. Instead, we adopt a novel strategy that
-aims to determine relative importance of the SW potential parameters based on derivative-based global 
-sensitivity measures (DGSM)~\cite{Sobol:2010}. It is observed that for a given application, it might be possible to 
+by estimating the so-called Sobol\textquotesingle~indices~\cite{Sobol:2001}. However, obtaining converged estimates of
+Sobol\textquotesingle~indices typically requires tens of thousands of model evaluations to be able to numerically approximate
+multi-dimensional integrals associated with the expectation and variance operators, especially in case $\bm{\theta}$,
+the vector of uncertain model inputs is high-dimensional:
+
+\be
+ \mathcal{T}_i = \frac{\mathbb{E}_{\bm{\theta}\sim i}[\mathbb{V}_{\theta_i}(\mathcal{G}|\bm{\theta}_{\sim i})]}{\mathbb{V}(\mathcal{G})} 
+ \ee
+
+ \noindent where $\mathcal{T}_i$ is the Sobol\textquotesingle~total-effect index, $\mathcal{G}$ denotes the model output,
+ $\mathbb{E}_{\bm{\theta}\sim i}[]$ is an expectation over all but the $i^{\mbox{th}}$ component of 
+ $\bm{\theta}$, and $\mathbb{V}_{\theta_i}()$ is the variance taken over $\theta_i$. Li and Mahadevan
+ recently proposed a computationally efficient method for estimating the first-order Sobol\textquotesingle~index~\cite{Li:2016}.
+However, since NEMD is compute-intensive,
+estimating the Sobol\textquotesingle~indices directly would be impractical in the present scenario. Hence, instead of 
+estimating Sobol\textquotesingle~sensitivity
+indices, we focus our attention on the upper bound of the Sobol\textquotesingle~total-effect index to determine the relative
+importance of SW potential parameters. 
+It is observed that for a given application, it might be possible to 
 converge to the upper bound on
-Sobol index with only a few iterations~($\mathcal{O}(10^{1})$). 
+Sobol\textquotesingle~index with only a few iterations~($\mathcal{O}(10^{1})$)~\cite{Kucherenko:2016}. 
 In that case, estimates of the upper bound could be used in lieu of the
-Sobol indices to determine relative importance of the parameters and hence reduce the associated computational
-effort by several order of magnitude. The upper bound on 
-Sobol total effect index\footnote{Sobol total effect index is a measure of the contribution of a 
-parameter to the variance of the observable while contribution from other parameters may or may not be 0.}
-($\mathcal{T}_i$) can be expressed in terms of DGSM~($\mu_i$), the Poincar\' e 
+Sobol\textquotesingle~indices to determine relative importance of the parameters and hence 
+reduce the associated computational
+effort by several order of magnitude. The upper bound of the
+Sobol\textquotesingle~total effect index\footnote{Sobol\textquotesingle~total effect index is a measure
+ of the contribution of an 
+input to the variance of the model output, also accounting for the contribution coupled with other inputs.}
+($\mathcal{T}_i$) can be expressed in terms of a derivative-based sensitivity measure~(DGSM), $\mu_i$, the Poincar\' e 
 constant~($\mathcal{C}_i$), and the total variance of the observed
@@
 defined as an expectation
-of the derivative of the observable ($G(\bm{\theta})$) with respect to that parameter:
+of the derivative of the output ($G(\bm{\theta})$) with respect to that parameter:
 
@@
 We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
-Sobol total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
+Sobol\textquotesingle~total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
 introduce small perturbations~($\mathcal{O}(10^{-5})n_i$; $n_i$ being the nominal value) to the nominal values
@@
 pertaining to the estimation of DGSM can be substantial, it is nevertheless several orders of magnitude smaller
-than directly estimating the Sobol indices as mentioned earlier. 
+than directly estimating the Sobol\textquotesingle~indices as mentioned earlier. 
 In Figure~\ref{fig:ub}, we plot $\hat{\mathcal{C}_i\mu_i}$ as obtained for the SW parameters at the 
@@
  \begin{center}
-  \includegraphics[width=0.70\textwidth]{./Figures/ub}
-\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 25(7+1)
+  \includegraphics[width=0.65\textwidth]{./Figures/ub}
+\caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 200
 points is plotted for each SW potential parameter.}
@@
 The surrogate enables forward propagation of uncertainty in the SW potential to the bulk thermal conductivity 
-estimates, and the estimation of Sobol sensitivity indices with minimal computational effort.
+estimates, and the estimation of Sobol\textquotesingle~sensitivity indices with minimal computational effort.

### 2018-04-29 Paper/setup.tex
..

@@
 
-Non-equilibrium molecular dynamics (NEMD) simulations are performed using LAMMPS~\cite{Plimpton:2007}.
+In this work, non-equilibrium molecular dynamics (NEMD) simulations are performed using the 
+LAMMPS~\cite{Plimpton:2007} software package.
 Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
@@
 
-There NEMD simulation has three stages associated with it as illustrated below in the flow diagram. In the
-first stage, the NVT ensemble equilibrates the system to a specified bulk temperature i.e. the temperature
+The NEMD simulation has three stages associated with it as illustrated below in the flow diagram. In the
+first stage, the NVT ensemble equilibrates the system to a specified bulk temperature, i.e., the temperature
 at which thermal conductivity is to be estimated. In the second stage, the NVE ensemble equilibrates the

### 2018-04-29 Slides/gen_slides.sh

@@ -1,5 +1,0 @@
-#!/bin/sh
-
-pdflatex md_si.tex
-pdflatex md_si.tex
-rm *.aux *.log *.out *.toc *.nav *.snm

### 2018-07-02 Paper/Rebuttal/rebuttal.tex
..

\documentclass[12pt]{article}
\input{def}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{enumitem}

%\usepackage[left=0.75in ,top=0.5in, bottom=0.5in, right=0.75in, footskip=0.5cm]{geometry}
\begin{document}

\parskip=6pt

\begin{center}
{\bf Summary of Modifications to HMT\_2018\_2060}\\[6pt]
{\bf Uncertainty Quantification in Non-Equilibrium Molecular Dynamics Simulations of Thermal Transport}\\[6pt]
By \\
Manav Vohra, Ali Yousefzadi Nobakht, Seungha Shin, Sankaran Mahadevan 
\end{center}

\baselineskip=22pt

\vspace*{1in}

We thank the reviewers for their assessment of our manuscript.
Below is a summary of modifications made to our original submission in
response to the reviewers suggestions.

Where possible, key modifications have been highlighted in blue in the revised
manuscript.

We hope that with these modifications
the paper is found suitable for publication in the {\it International Journal of Heat and Mass Transfer}.

\clearpage

\section*{Referee 1}
\begin{enumerate}[leftmargin=*,itemsep=24pt]
\item \textbf{Comment 1}

\end{enumerate}

%\bibliographystyle{unsrt}
%\bibliography{REFER}

\end{document}

### 2018-07-04 Paper/sense.tex
..

@@
 are dependent on the choice of the inter-atomic potential as well as values associated with
-the individual potential parameters. In the case of silicon, the Stillinger-Weber inter-atomic potential
-has been used for a wide variety of 
-systems~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein).
-However, according to Stillinger and Weber, the set of nominal
-values as provided below in Table~2 were based on a constrained search in the 7D parameter space
-to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.
+the individual potential parameters. In the case of silicon, the Stillinger-Weber (SW)
+is a commonly used inter-atomic potential~(see~\cite{Laradji:1995,Zhang:2014,Jiang:2015,Watanabe:1999,Zhou:2013} and references therein). \rev{Functional form of the SW potential is given as follows:
+%
+\be
+\Phi = \sum\limits_{i,j(i<j)}\phi_2(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}\phi_3(\lambda,\gamma)
+\ee
+%
+where $\phi_2$ and $\phi_3$ represent two-body and three-body atomic interactions 
+respectively~\cite{Stillinger:1985}.}
+
+Although the SW potential is used for a wide variety of Si systems, 
+according to Stillinger and Weber, the set of nominal
+values as provided below in Table~2 were based on a constrained search in the 7D parameter space to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}.
 

### 2018-07-04 Paper/setup.tex
..

@@
 LAMMPS~\cite{Plimpton:2007} software package.
-Essentially, a thermal gradient is applied by means of thermostats located at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
+Essentially, a thermal gradient is applied by means of \rev{Langevin} thermostats located
+at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
 as shown using a schematic in Figure~\ref{fig:setup}.
@@
 $\Delta t$  (ps) & 0.0005 \\ \hline
+\rev{Simulation Run Length (ps)} & \rev{320} \\ \hline
 Boundary Condition & Periodic \\ \hline

### 2018-07-05 Paper/Rebuttal/rebuttal.tex
..

@@
 \begin{enumerate}[leftmargin=*,itemsep=24pt]
-\item \textbf{Comment 1}
+\item \textbf{It is worth having some detailed on NEMD for example, what thermostats were used, 
+numbers of atoms, and length of simulations etc.}
+
+This suggestion has been incorporated in the revised manuscript.
+
+\item \textbf{The readers would appreciate if the authors add original potential equation for SW (rather than
+showing Table 2 without having equation)$?$}
+
+This suggestion has been incorporated in the revised manuscript.
+
+\item \textbf{It is recommended to justify (or discuss) why the authors chose the specific numbers of sample.
+Also, the system size is very critical to calculate the thermal conductivity using NEMD, and it is
+worth justifying the choice of system size for NEMD.}
+
+As suggested by the referee, we have justified the choice of the number of samples in the revised manuscript.
+Regarding the choice of system size, we have emphasized in the revised manuscript that the focus of this
+work is on demonstrating an efficient methodology for quantifying the uncertainties in NEMD predictions
+within a limited computational budget. The considered range for system size is found to be sufficient for
+this purpose.
+
+\end{enumerate}
+
+\section*{Referee 2}
+\begin{enumerate}[leftmargin=*,itemsep=24pt]
+\item \textbf{The range of parameters considered in the study is quite limited (L: five values in the range of 50a ~ 100a; dT/dz: five values in the range of 1.5/a ~ 2.5/a).
+Since both L and dT/dz vary by at most a factor of two, the subsequent analyses and the conclusions drawn based on the analyses could be biased.
+For a more thorough uncertainty quantification study, a larger sample size is likely needed, and the parameters would need be varied by larger extents.
+For L, one possible reference is the effective phonon mean path.
+For dT/dz, a lower bound could be some value larger than the noise level of MD simulations.}
+
+We would like to emphasize that the focus of this work is on demonstrating a methodology for quantifying the
+uncertainty in NEMD predictions. Specifically, in the initial part, we develop efficient response surfaces
+to capture the relationship between simulation inputs: length, temperature gradient and the discrepancy in
+bulk thermal conductivity predictions. Note that we do not aim to enhance the accuracy of NEMD predictions.
+Moreover, the proposed methodology accounts for limitated availability of computational resources. The
+consider range of system size is found to be suitable for this purpose. In order to avoid MD noise, we
+have used average temperature at the bin point during the data production NVE ensemble. Hence, the
+impact of noise on NEMD predictions in the considered range for $\frac{dT}{dz}$ is found to be negligible.
+
+The above points have been emphasized in the revised manuscript. A justification for the choice of 5 points
+along $L$ and $\frac{dT}{dz}$ has also been included.
+
+\item \textbf{The authors mentioned in a few places the fluctuations in the applied thermal gradient (e.g., Line 9 from the bottom on Page 4).
+This is not very clear to the reviewer.
+Do the authors mean different applied thermal gradients?
+By the way, the term “thermal gradient” is typically referred to as “temperature gradient”.
+If the temperature gradient is evaluated in regions far away from the thermostats (e.g., around z = 0.5L in Fig.
+2), would the thermostats affect the temperature gradients?}
+
+Significant temperature fluctuations are observed especially in the vicinity of the thermostats in our setup
+as shown in Figure 2. As a result, it is possible that the temperature gradient experienced by the
+system is different from that specified in the input. Hence, the applied temperature gradient is also considered
+to be a potential source of uncertainty in our analysis. We have attempted to clarify this in the revised
+manuscript.
+
+As suggested by the referee, ``thermal gradient" has been replaced with ``temperature gradient" in the 
+revised manuscript.
+
+The impact of thermostating on the temperature gradient is expect to decay with distance from the thermostats
+as observed in Figure 2.
+
+\item \textbf{For the NEMD simulations, what is the total simulation time?
+Another comment is about the system size in the width and height directions.
+Based on the reviewer’s experience, the NEMD calculated thermal conductivities are not very sensitive to the domain sizes in the width and height directions.
+Usually using a size around 5a for the width and height would be sufficient.
+This could be taken into account to reduce the simulation time.}
+
+Simulation time has been included in the revised manuscript (Table 1) as suggested by the referee. As pointed
+out by the referee, the impact of width and height was not found to be significantly large. 
+As discussed in the manuscript, the choice of width and height in this study was an outcome of a careful
+analysis aimed at minimizing temperature fluctuations during different stages in the NEMD simulation. As
+suggested by the referee, a smaller width and height could have been used to further reduce computational
+effort.
+
+\item \textbf{For Si, previous results show that the phonon mean free path could span a wide range (e.g., from 10-2 to 103 um, see for example Fig.
+11 of J.
+Comput.
+Theor.
+Nanosci.
+5, 1–12, (2008)).
+When comparing the NEMD simulation domain size with the phonon mean free path, the authors should take this into account.}
+
+We acknowledge the referee's input and are aware that thermal conductivity in NEMD is dependent on the 
+dimension of simulation domain since phonons with longer mean free path can be ballistically transported.
+Hence, the bulk thermal conductivity is estimated by extrapolating the relationship between the
+inverse of conductivity and the inverse of system size as illustrated in Figure 5.
+
+\item \textbf{When conducting the sensitivity analysis, the authors considered very small fluctuations ~O(10-5)*ni.
+Could the authors comment on the possible effects of larger fluctuations (e.g., 1$\%$ or 10$\%$)$?$}
+
+We would like to clarify that small perturbations in the nominal estimates of the Stillinger-Weber (SW)
+potential parameters are introduced to estimate the partial derivatives in Eq.8 with reasonable accuracy using
+finite difference. In fact, the prior intervals for the SW parameters are considered to be $\pm 10\%$ for the
+purpose of sensitivity analysis and constructing a reduced order surrogate as mentioned in section 5.
+
+\item \textbf{Many of the results (e.g., Figs.
+5 and 9) in the manuscript essentially show internal consistency.
+It would be helpful if the authors could check whether the results could be extended to cases outside the considered parameter ranges (i.e., to check the predictive power of the model analysis).
+The purpose of uncertainty quantification should be understanding what affects the uncertainty in the final results, so that people can actively control or accurately report the uncertainties.
+A predictive model would be more valuable to the fellow researchers.}
+
+The referee makes an important point. However, we would like to point out that the overall objective of the
+proposed methodology is calibration of the inter-atomic potential using a Bayesian framework. To
+reduce computational effort, we construct efficient surrogates in Figures 5 and 9. Note that the accuracy
+of the surrogates is tightly coupled with the choice of training points that essentially lie within the
+considered intervals for length and the temperature gradient in one case and the SW potential parameters
+in the other case. Hence, the surrogates can be reliably used only for the purpose of sensitivity analysis
+and calibration in the considered input domain. A predictive model while certainty useful is beyond the
+scope of this work. Additionally, verifying the accuracy of the surrogates outside the considered domain 
+would involve large computational effort and is not expected to enhance the proposed methodology in this work.
+
+\item \textbf{The reviewer would like to point out one relevant paper (IJHMT 112, 267-278 (2017)), which studies the uncertainty quantification of EMD predicted thermal conductivities.}
+
+Suggested reference has been cited appropriately in the revised manuscript.
+
+\item \textbf{In Eq. (1), the numerator should be q’’, meaning heat flux (W/m2).}
+
+Referee's suggestion has been incorporated in the revised manuscript.
+
+\item \textbf{The abbreviations (e.g., PC, DGSM) need only be explained in the first occurrence.}
+
+This suggestion has been incorporated in the revised manusctript.
+
+\item \textbf{In Fig. 5, it is worth checking whether the extrapolating L-1 to 0 will give the expected k for bulk Si.}
+
+Figure 5 has been updated and the extrapolated bulk thermal conductivity estimates have been reported in the
+revised manuscript.
 

### 2018-07-05 Paper/abstract.tex
..

\section*{Abstract}

Bulk thermal conductivity estimates based on predictions from non-equilibrium molecular dynamics (NEMD)
using the so-called direct method are known to be severely under-predicted since finite simulation
length-scales are unable to mimic bulk transport. Moreover, subjecting the system to a temperature gradient
by means of thermostatting tends to impact phonon transport adversely.  Additionally, NEMD predictions
are tightly coupled with the choice of the inter-atomic potential and the underlying values associated with its
parameters. In the case of silicon (Si), nominal estimates of the Stillinger-Weber (SW) potential parameters are largely based 
on a constrained regression approach aimed at agreement with experimental data while ensuring structural
stability. However, this approach has its shortcomings and it may not be ideal to use the same set of parameters
 to study a wide variety of Si-based
systems subjected to different thermodynamic conditions. 
In this study, NEMD simulations are performed on a Si bar to investigate the impact of bar-length,
and the applied temperature gradient on the discrepancy between predictions and the available measurement 
for bulk thermal conductivity at 300~K by constructing statistical response surfaces at different temperatures. 
The approach helps quantify the discrepancy, observed to be largely dependent on the system-size, with minimal
computational effort. A computationally efficient approach based on derivative-based sensitivity measures to
construct a reduced-order polynomial chaos surrogate for NEMD predictions is also presented. The surrogate
is used to perform parametric sensitivity analysis, forward propagation of the uncertainty, and calibration of the important SW potential parameters in a 
Bayesian setting. It is found that only two (out of seven) parameters contribute significantly to the uncertainty
in bulk thermal conductivity estimates for Si.

### 2018-07-05 Paper/disc.tex
..

@@
 In this paper, we have attempted to identify and address some of the challenges
-pertaining to uncertainty analysis of bulk thermal conductivity predictions 
+pertaining to uncertainty quantification of bulk thermal conductivity predictions 
 using non-equilibrium molecular dynamics (NEMD) simulations. Specifically, we focused
-on investigating the impact of system size, and variability in the applied thermal
+on investigating the impact of system size, and fluctuations in the applied temperature
 gradient on predictions. In order to quantify the discrepancy between NEMD
@@
 It was found that the discrepancy is predominantly impacted by size while the 
-effect of variability in the applied thermal gradient is negligible in the considered
+effect of fluctuations in the applied temperature gradient is negligible in the considered
 interval. The response surface approach presented here relies on a small number of
@@
 and a point in the 2D parameter space described by system-size and the applied
-thermal gradient.
+temperature gradient.
 
@@
 we focus our efforts on understanding the sensitivity of predictions on individual potential
-parameters. For this purpose, we estimate the so-called derivative based sensitivity
-measures (DGSM) using random samples in the 7D parameter space. While individual
-measures for the 7 parameters are not too distant from each other, the predictions
+parameters. In order to reduce the computational effort, we estimate the DGSMs
+ and hence the upper bound
+on Sobol\textquotesingle~total-effect sensitivity index using random samples in the 7D parameter space. 
+While individual measures for the 7 parameters are not too distant from each other, the predictions
 seem to be most sensitive towards $\gamma$. Sensitivity measures for $\alpha$,
@@
 computational effort required for forward propagation of the uncertainty from
-parameters to the observable as well as for estimating the Sobol sensitivity indices.
+parameters to the observable as well as for estimating the Sobol\textquotesingle~sensitivity indices.
 Furthermore, the surrogate could be used to accelerate parameter calibration in a
@@
 this challenge, we exploit our initial findings based on DGSM and construct
-a reduced order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
+a reduced-order surrogate in 5 dimensions by fixing the parameters, $B$ and $p$.
 We verify its accuracy by estimating the relative
-L-2 norm of the error between NEMD predictions in the full space and the reduced
-order surrogate predictions, and comparing the probability distribution of the
+L-2 norm of the error between NEMD predictions in the full space and the reduced-order
+surrogate predictions, and by comparing the probability density of the
 bulk thermal conductivity in Figure~\ref{fig:verify}. Furthermore, our initial
 sensitivity trends based on DGSM-analysis using 25 samples seem to agree favorably
-with Sobol sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
+with Sobol\textquotesingle~sensitivity analysis based on 10$^{6}$ samples. Hence, it can be said
 that DGSM-based analysis with a few samples could offer huge computational gains
@@
 steps: First, perform DGSM analysis to 
-identify parameters that are not so important. Second, construct a reduced order
-surrogate based on DGSM-analysis. Third, verify the accuracy of the surrogate
-and compute Sobol indices. Fourth, consider only the important parameters in
-calibration and construct a second surrogate in the reduced subspace. Fifth,
-quantify the surrogate error to be accounted for during calibration. Sixth,
-evaluate the joint posterior using an efficient MCMC-based algorithm.
+identify parameters that are not so important. Second, construct a reduced-order
+surrogate based on DGSM-analysis and verify its accuracy. Third, compute the
+Sobol\textquotesingle~sensitivity indices using the surrogate to identify parameters for calibration. 
+Fourth, construct a second surrogate in the reduced subspace described by the
+calibration parameters, and quantify the surrogate error to be accounted for
+in calibration. Fifth, evaluate the joint posterior using an efficient MCMC-based algorithm
+such as adaptive Metropolis~\cite{Haario:2001} and its variants~\cite{Haario:2006, Green:2001}.
 
-In conclusion, the authors would like to highlight that the strategies presented 
+It is important to note that the strategies presented 
 in this work are not restricted to a Si bar and the Stillinger-Weber potential, and
 could be extended to a wide range of applications and inter-atomic potentials for
-the purpose of uncertainty analysis.
+the purpose of uncertainty quantification.

### 2018-07-05 Paper/intro.tex
..

@@
 Predictions impacted by the choice of potential, values of
-individual parameters, size, and potentially due to duration and applied thermal gradients
+individual parameters, size, and potentially due to duration and applied temperature gradients
 (cite Amuthan book, Francesco's paper, McGaughey's paper). 
@@
 different atoms potentially reducing the thermal conductivity
-further~\cite{Evans:2008}. Estimation of thermal conductivity using the
+further~\cite{Evans:2008}. \rev{The average temperature gradient experienced by the 
+system could thus be different from the simulation input and is a potential source of 
+uncertainty.} Estimation of thermal conductivity using the
 direct method is therefore impacted by the choice of system size and potentially due to
-fluctuations in the thermal gradient experienced by the system due to thermostatting.
+fluctuations in the temperature gradient experienced by the system due to thermostatting.
 
@@
 wide variety of Si-based systems and warrant further investigation to study the impact of
-underlying uncertainties on MD predictions. Along these lines, 
-a recent study by Rizzi et al. focused on the effect of
+underlying uncertainties on MD predictions. \rev{Along these lines, 
+a recent study by Wang et al. performed uncertainty quantification of thermal conductivities
+from equilibrium molecular dynamics simulations~\cite{Wang:2017}}.
+Rizzi et al. focused on the effect of
 uncertainties associated with the force-field parameters on bulk water properties using MD
@@
 exhibit large discrepancies with experimental observations depending upon system size and potentially
-due to fluctuations in the applied thermal gradient. Additionally, the thermal conductivity estimates are
+due to fluctuations in the applied temperature gradient. Additionally, the thermal conductivity estimates are
 tightly coupled with parameter values associated with the inter-atomic potential. Hence, we set out to
@@
 in order to characterize the dependence of discrepancy in thermal conductivity estimates (between
-MD simulations and experiments) on system size, and applied thermal gradient~(Section~\ref{sec:response}).
+MD simulations and experiments) on system size, and applied temperature gradient~(Section~\ref{sec:response}).
 Second, we perform sensitivity analysis to study the impact of SW potential parameter values on 

### 2018-07-05 Paper/sense.tex
..

@@
 
-We aim to compute the derivative-based sensitivity measure (DGSM) and hence the corresponding upper bound on the
+We aim to compute the DGSM and hence the corresponding upper bound on the
 Sobol\textquotesingle~total effect index~($\mathcal{T}_i$) for each parameter in the SW potential. For this purpose, we 
@@
  \begin{center}
-  \includegraphics[width=0.65\textwidth]{./Figures/ub}
+  \includegraphics[width=0.5\textwidth]{./Figures/ub}
 \caption{The quantity $\hat{\mathcal{C}_i\mu_i}$ as computed after 4 iterations and data at 200

### 2018-07-05 Paper/setup.tex
..

@@
 LAMMPS~\cite{Plimpton:2007} software package.
-Essentially, a thermal gradient is applied by means of \rev{Langevin} thermostats located
+Essentially, a temperature gradient is applied by means of \rev{Langevin} thermostats located
 at $L$/4 and $3L$/4 in a silicon bar of length, $L$ 
@@
 \caption{(a) Schematic illustration of the set-up for evaluating thermal conductivity of Si using NEMD. (b) 
-Arrangement of Si atoms prior to the application of thermal gradient.}
+Arrangement of Si atoms prior to the application of temperature gradient.}
 \label{fig:setup}
@@
 inputs to LAMMPS is provided below in Table~\ref{tab:input}. Note that specific values for the length of the bar
-and the applied thermal gradient are not provided since we investigate thermal conductivity trends for a range of 
+and the applied temperature gradient are not provided since we investigate thermal conductivity trends for a range of 
 values of the two parameters as discussed later in Section~\ref{sec:response}. A careful analysis focused on
@@
 \be
- \kappa = \frac{q}{\left|\frac{dT}{dz}\right|} 
+ \kappa = \frac{\rev{q''}}{\left|\frac{dT}{dz}\right|} 
 \ee
 
-\noindent where $\left|\frac{dT}{dz}\right|$ denotes the magnitude of the applied temperature gradient along the 
-direction of heat flow (see~Figure~\ref{fig:setup}(a)).
+\noindent where \rev{$q''$ denotes the steady state heat flux (W/m$^2$)} and
+$\left|\frac{dT}{dz}\right|$ denotes the magnitude of the applied 
+temperature gradient along the direction of heat flow (see~Figure~\ref{fig:setup}(a)).
